---
title: "RHESSysIOinR_Coweeta_WS32_74 Multi Site Validation Field Data_Step2"
author: "Carlos Quintero"
date: "5/24/2024"
output:
  html_document: default
  pdf_document: default
---
```{r include=FALSE}
knitr::opts_knit$set(root.dir = system.file("extdata/", package = "RHESSysIOinR"))
 setwd(system.file("extdata/", package = "RHESSysIOinR"))
```

Coweeta Hydrologic Laboratory Watershed 32 using Static, SSURGO, and RSS soil inputs. 

The following R Markdown script prepares and runs the Regional Hydro-Ecologic Simulation System (RHESSYS) within the R environment. 
Modified from RHESSysIOinR example scripts created by Will Burke and Ryan Bart. Includes CLHS code snippets and SDA code from Dylan Beaudette.

Windows Subsystem via Linux must be installed before RHESSys will run in a Windows environment.
GRASS8 must be installed to run the spatial preprocessing portion of the script.

Code has been modified to run RHESSys 7.4 and 5.18. 
7.4 vegetation processing differs slightly from 5.18.
Various template differences exist between the two versions of RHESSys and template files must be carefully reviewed if moving between versions.
This script is currently set up to run RHESSys 7.4

```{r setup, include=TRUE, verbose = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#install.packages("devtools")
#devtools::install_github("ropensci/FedData")

library(aqp)
library(daymetr)
library(clhs)
library(EcoHydRology)
library(elevatr)
library(ezknitr)
library(FedData)
library(foreach)
library(foreign)
library(ggplot2)
library(ggpubr)
library(hydroGOF)
library(imputeTS)
library(knitr)
library(latticeExtra)
library(lubridate)
library(Metrics)
library(raster)
library(rasterVis)
library(readxl)
library(reshape2)
library(rgdal)
library(rgrass)
library(rmarkdown)
library(Rmisc)
library(RHESSysPreprocessing)
library(RHESSysIOinR)
library(sf)
library(soilDB)
library(sp)
library(stats)
library(stringi)
library(tactile)
library(terra)
library(testthat)
library(tidyverse)
library(viridisLite)
library(dplyr)



#knitr::opts_knit$set(root.dir = system.file("extdata/", package = "RHESSysIOinR"))
 setwd(system.file("extdata/", package = "RHESSysIOinR"))
 
### Downloads most recent version of RHESSYs
# gert::git_clone(url = "https://github.com/RHESSys/RHESSys", path = "/modelfiles/rhessys", branch = "trunk")

# compile_rhessys(location = "modelfiles/")

rh_ver = dir(path = "modelfiles/rhessys/", pattern = "^rhessys\\d+",recursive = F)

getwd()

rh_path = file.path("modelfiles/rhessys", rh_ver)

## Load in necessary files
filedir <- ("C:/Users/Carlos/Documents/GitHub/RHESSys74-R-Markdown/")

watershedshapefile <- paste0(filedir, "input_files/shapefiles/watersheds/Coweeta_Hydrologic_Laboratory.shp")
streamshapefile<- paste0(filedir,"input_files/shapefiles/streams/StreamsCaldwellClipped.shp")
weirshapefile<- paste0(filedir,"input_files/shapefiles/weirs/Subbasinoutlets.shp")
roadshapefile <- paste0(filedir, "input_files/shapefiles/roads/UpdatedRoads4Reprojected32617.shp")

CWRG12 <- paste0(filedir,"input_files/precipitation/RDS-2017-0031/Data/RG12_daily_1942_2021.csv")
CWRG20 <-paste0(filedir,"input_files/precipitation/RDS-2017-0031/Data/RG20_daily_1962_2021.csv")

CS01 <- ("C:/Users/Carlos/Desktop/ORISE/Climate Data/CW/Air Temperature/CS01 OISHI/cs01_hourly_Tair_2011_2023.csv")
CS01LT<- ("C:/Users/Carlos/Desktop/ORISE/Climate Data/CW/Air Temperature/RDS-2015-0049/Data/cs01_daily_airtemp.csv")
CS21<- paste0(filedir,"input_files/temperature/RDS-2015-0042/Data/cs21_daily.csv")
CS28<- paste0(filedir,"input_files/temperature/RDS-2015-0042/Data/cs28_daily.csv")

newsmlocations<-  paste0(filedir,"input_files/shapefiles/soil_moisture/CoweetaNRCSsmKML.kml")

```

Setup RHESSys Inputs/Outputs for Spinup
Note that flowtable is converted flowtable. Using original flow table will result in errors.

Original spinup 0219 to 2017. Modified output to 1776-2017 to test code without very long spin-up.
Climate files have been modified to original DAYMET timeseries. 

```{r RHESsys Spinup Configuration}
setwd(system.file("extdata/", package = "RHESSysIOinR"))
## Read climate file to see length available climate data
read_clim("clim/cwtws32extended.rain", dates_out=TRUE)
read_clim("clim/cwtws32local.rain", dates_out=TRUE)

# Begin RHESSys Spinup
##Short Spinup, original spinup run 1776-2018

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32.world",
  world_hdr_prefix = "CWWS32",
  flowtable = "CWWS321.flow",
  start = "1775 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32",
  commandline_options = c("-b -g"))

input_tec_data = IOin_tec_std(start = "1776 11 1 1",
                              end = "2018 11 1 1",
                              output_state = TRUE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32extended.base")

##suggested standard hydrologic spinup parameters from rhessys wiki, gw values modified based on previous results from Coweeta Landscape

stdpars<- IOin_cmd_pars( 
            m = 1,
            k = 10,
            soil_dep= 0.4,
            m_v = 1,
            k_v = 1,
            gw1 = 0.15,
            gw2 = 0.35)


```

Run Spinup #1

Spinup runs model on one processor for x number of years. Takes a very long time. 

Spinup has been turned off for the purposes of this demonstration. Using previously spun up file ~ 12 hours, run multiple times.

```{r Spinup Run, eval=FALSE, include=FALSE}

start_time = Sys.time()
run_rhessys_single(input_rhessys = input_rhessys,
                   hdr_files = input_hdr,
                   tec_data = input_tec_data,
                   def_pars = stdpars,
                   runID = 'spinup')
end_time = Sys.time()
end_time - start_time

```

Run Spinup again, Run Spinup #2

```{r Spinup again with created worldfile, eval=FALSE, include=FALSE}

setwd(system.file("extdata/", package = "RHESSysIOinR"))


input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32.world.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32",
  flowtable = "CWWS321.flow",
  start = "1775 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32",
  commandline_options = c("-b -g"))


start_time = Sys.time()
run_rhessys_single(input_rhessys = input_rhessys,
                   hdr_files = input_hdr,
                   tec_data = input_tec_data,
                   std_pars = stdpars,
                   runID = 'spinup')
end_time = Sys.time()
end_time - start_time


```

Read Spinup and confirm that Soil C and Soil N have stabilized

```{r Read RHESSys Spinup}
setwd(system.file("extdata/", package = "RHESSysIOinR"))
spinupoutput<- readin_rhessys_output("out/cwws32dsm_rundsmspinup")
#spinupoutput<- readin_rhessys_output("out/cwws32ssurgo_runssurgospinup")

spinupoutput$bd$date <- make_date(year=spinupoutput$bd$year, month = spinupoutput$bd$month, day = spinupoutput$bd$day)
spinupoutput$bdg$date <- make_date(year=spinupoutput$bdg$year, month = spinupoutput$bdg$month, day = spinupoutput$bdg$day)

range(spinupoutput$bd$year)

plot(spinupoutput$bd$streamflow, type = "l")

plot(spinupoutput$bd$date,spinupoutput$bd$streamflow, type = "l", col = 'black', main = "Predicted Streamflow",
    xlab = "Date", ylab = "Streamflow mm")

plot(spinupoutput$bdg$date, spinupoutput$bdg$lai, type = "l", main = "LAI", xlab = "Date")
{plot(spinupoutput$bdg$soilc~spinupoutput$bdg$date,type = "l", main = "Spinup Soil Carbon", xlab = "Date")
soilctrend <- glm(spinupoutput$bdg$soilc~spinupoutput$bdg$date)
abline(soilctrend, col = 'red')}
{plot(spinupoutput$bdg$date,spinupoutput$bdg$soiln, type = "l", main = "Spinup Soil Nitrogen", xlab = "Date")
soilntrend <- glm(spinupoutput$bdg$soiln~spinupoutput$bdg$date)
abline(soilntrend , col = 'green')}

#prepped<- readin_rhessys_output("G:/Coweeta W32/output/basicspinupws32")

```

Configure RHESSys Inputs/Outputs for a single run.

Use World Statefile created during spin-up. To run model one time at patch scale.

 COMMAND LINE OPTIONS

-b		Basin output option.  Print out response variables for specified basins. 
-c		Canopy stratum output option.  Print out response variables for specified strata. 
-g		Grow option.  Try to read in dynamic bgc input data and output dynamic bgc parameters. 
-h    Hillslope output option.  Print out response variables for specified hillslopes. 
-p		Patch output option.  Print out response variables for specified patches. 
-r		Routing option. Gives name of flow_table to define explicit routing connectivity.  Also trigger use of explicit routing over TOPMODEL approach. 
-c		Stratum output option.  Print out response variables for specified strata. 

```{r Configure RHESSys Inputs using Created Worldfile}

read_clim("clim/cwtws32daymet.rain", dates_out = TRUE)

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32dsm.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32dsm",
  flowtable = "CWWS32dsm1.flow",
  start = "2014 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32dsm",
  commandline_options = c("-b -p"))

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created

input_tec_data = IOin_tec_std(start = "2015 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")

stdpars<- IOin_std_pars(
            m = 1.75,
            k = 18.69,
            soil_dep= 0.48,
            m_v = 2.55,
            k_v = 7.54,
            gw1 = 0.19,
            gw2 = 0.29,
            pa = 0.17,
            po = 1.02,
            vgseng1 = 1.61,
            vgseng2 = 1.94,
            vgseng3 = 0.72)

```

Run RHESSys once

```{r Run Rhessys Once, include=FALSE}

start_time = Sys.time()
start_time
run_rhessys_single(input_rhessys = input_rhessys,
                   hdr_files = input_hdr,
                   tec_data = input_tec_data,
                   std_pars = stdpars,
                   runID = 'single')
end_time = Sys.time()
end_time - start_time
end_time

```

Run RHESSys once with output filter

```{r}
setwd(system.file("extdata/", package = "RHESSysIOinR"))

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32dsm.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32dsm",
  flowtable = "CWWS32dsm1.flow",
  start = "2014 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32dsm",
  commandline_options = c())

input_tec_data = IOin_tec_std(start = "2015 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")

stdpars<- IOin_std_pars(
            m = 1.75,
            k = 18.69,
            soil_dep= 0.48,
            m_v = 2.55,
            k_v = 7.54,
            gw1 = 0.19,
            gw2 = 0.29,
            pa = 0.17,
            po = 1.02,
            vgseng1 = 1.61,
            vgseng2 = 1.94,
            vgseng3 = 0.72)


#patch.streamflow + hill.gw.Qout


patchfilter <- build_output_filter(timestep = "daily", output_format= "csv", output_path = "../out", output_filename = "testfbasinstreamflow", spatial_level = "basin",spatial_ID = "1", variables = "patch.total_water_in" )

patchfilter


patchfilter2<- read_output_filter("tecfiles/testing_filter2.yml")

patchfilter2




start_time = Sys.time()
start_time
run_rhessys_single(input_rhessys = input_rhessys,
                   hdr_files = input_hdr,
                   tec_data = input_tec_data,
                   std_pars = stdpars,
                   output_filter = patchfilter,
                   runID = 'single')
end_time = Sys.time()
end_time - start_time
end_time


```


Read RHESSys Single Run Output

```{r Read in RHESSys Output}

getwd()

singleruntest<- readin_rhessys_output("out/cwws32_runsingle")

plot(singleruntest$bd$streamflow~singleruntest$bd$date, type = "l", main = "Streamflow", xlab = "Date", ylab = "Streamflow", col = 'DarkBlue')

plot(as.Date(singleruntest$bd$date),singleruntest$bd$rz_storage, type = "l", col = 'black', main = "Basin Scale Root Zone Storage",
    xlab = "Date", ylab = "mm")

#basin scale soil moisture
plot(singleruntest$bd$rz_storage/singleruntest$bdg$root_depth~singleruntest$bd$date, type = "l", main = "RZ_Storage/Root_Depth x Date", xlab = "Date", ylab = "rz_Storage/root_depth", col = 'brown')

plot(singleruntest$bd$lai~singleruntest$bd$date, type = "l", main = "LAI", xlab = "Date", ylab = "LAI", col = 'DarkGreen')
plot(singleruntest$bd$pet~singleruntest$bd$date, type = "l", main = "Potential Evapotranspiration", xlab = "Date", ylab = "PET", col = 'DarkBlue')
plot(singleruntest$bd$et~singleruntest$bd$date, type = "l", main = "Evapotranspiration", xlab = "Date", ylab = "ET", col = 'darkslategray')

plot((singleruntest$bd$unsat_stor/singleruntest$bd$sat_def_z)~singleruntest$bd$date, type = "l", main = "unsat_stor/sat_def_z", xlab = "Date", ylab = "vwc", col = 'DarkGreen')


```

Plot and Filter Observed Soil Moisture

```{r Read, Filter and Plot Observed Soil Moisture}

## Data has not been pre-prepared and must be cleaned

smws32_1<- read.delim("C:/Users/Carlos/Desktop/ORISE/Soil Moisture Data/CW/knb-lter-cwt.1308.19/CWT_132_1_0.txt", header = T)
smws32_2<- read.delim("C:/Users/Carlos/Desktop/ORISE/Soil Moisture Data/CW/knb-lter-cwt.1308.19/CWT_232_1_1308.txt", header = T)
smws32_3<- read.delim("C:/Users/Carlos/Desktop/ORISE/Soil Moisture Data/CW/knb-lter-cwt.1308.19/CWT_332_1_1308.txt", header = T)

smws32_1$Date<- as.Date(smws32_1$Date)
smws32_2$Date<- as.Date(smws32_2$Date)
smws32_3$Date<- as.Date(smws32_3$Date)

smws32_1 <- smws32_1[,!sapply(smws32_1,is.character)]
smws32_2 <- smws32_2[,!sapply(smws32_2,is.character)]
smws32_3 <- smws32_3[,!sapply(smws32_3,is.character)]

#range(smws32_3$smois30A)

smws32_1mean<- aggregate(smws32_1, by = list(smws32_1$Date), FUN = function(x) mean(x, na.rm = TRUE))
smws32_2mean<- aggregate(smws32_2, by = list(smws32_2$Date), FUN = function(x) mean(x, na.rm = TRUE))
smws32_3mean<- aggregate(smws32_3, by = list(smws32_3$Date), FUN = function(x) mean(x, na.rm = TRUE))

smws32_1mean <- smws32_1mean[order(smws32_1mean$Date),]
smws32_2mean <- smws32_2mean[order(smws32_2mean$Date),]
smws32_3mean <- smws32_3mean[order(smws32_3mean$Date),]

#Filter Soil Moisture Datasets

smws32_1mean  <- smws32_1mean[smws32_1mean$smois30A>'0',]
smws32_3mean  <- smws32_3mean[smws32_3mean$smois30A<='0.45',]
smws32_3mean  <- smws32_3mean[smws32_3mean$Date<='2018-05-15',]


plot(smws32_1mean$Group.1,smws32_1mean$smois30A, type = "l", main = "Soil Moisture 30cm Site 1", xlab = "Date", ylab = "Soil Moisture 30A")
plot(smws32_2mean$Group.1,smws32_2mean$smois30A, type = "l", col = "blue", main = "Soil Moisture 30cm Site 2", xlab = "Date", ylab = "Soil Moisture 30A")
plot(smws32_3mean$Group.1,smws32_3mean$smois30A, type = "l", col = "red", main = "Soil Moisture 30cm Site 3", xlab = "Date", ylab = "Soil Moisture 30A")


{plot(smws32_1mean$Group.1,smws32_1mean$smois30A, type = "l", col = "red", ylim = c(0,0.4), xlab = "Date", ylab = "Soil Moisture", main = "Observed Soil Moisture WS32 30cm")
lines(smws32_2mean$Group.1,smws32_2mean$smois30A, type = "l", col = "blue", ylim = c(0,0.4))
lines(smws32_3mean$Group.1,smws32_3mean$smois30A, type = "l", col = "black", ylim = c(0,0.4))
legend("topright",inset = 0.05, legend=c("SM1","SM2","SM3"), col=c("red","blue","black"), lty=1)}


smws32_1mean  <- smws32_1mean[smws32_1mean$Date>='2017-01-01',]
smws32_2mean  <- smws32_2mean[smws32_2mean$Date>='2017-01-01',]
smws32_3mean  <- smws32_3mean[smws32_3mean$Date>='2017-01-01',]

smws32_1mean  <- smws32_1mean[smws32_1mean$Date<='2018-05-15',]
smws32_2mean  <- smws32_2mean[smws32_2mean$Date<='2018-05-15',]
smws32_3mean  <- smws32_3mean[smws32_3mean$Date<='2018-05-15',]

{plot(smws32_1mean$Group.1,smws32_1mean$smois30A, type = "l", col = "red", ylim = c(0,0.4), xlab = "Date", ylab = "Soil Moisture", main = "Truncated Observed Soil Moisture WS32 30cm")
lines(smws32_2mean$Group.1,smws32_2mean$smois30A, type = "l", col = "blue", ylim = c(0,0.4))
lines(smws32_3mean$Group.1,smws32_3mean$smois30A, type = "l", col = "black", ylim = c(0,0.4))
legend("topright",inset = 0.05, legend=c("SM1","SM2","SM3"), col=c("red","blue","black"), lty=1)}


{plot(density(smws32_1mean$smois30A), ylim = c(0,14), xlim = c(0,0.35), col = 'red', main = "Density of Observed Soil Moisture WS32 30cm")
lines(density(smws32_2mean$smois30A), col = 'blue')
lines(density(smws32_3mean$smois30A), col = 'black')
legend("topright",inset = 0.05, legend=c("SM1","SM2","SM3"), col=c("red","blue","black"), lty=1)}


{plot(smws32_1mean$Group.1,smws32_1mean$smois30A, type = "l", col = "red", ylim = c(0,0.4), xlab = "Date", ylab = "Soil Moisture", main = "Truncated Observed Soil Moisture WS32 Station 1")
lines(smws32_1mean$Group.1,smws32_1mean$smois30B, type = "l", col = "orange", ylim = c(0,0.4))
lines(smws32_1mean$Group.1,smws32_1mean$smois60A, type = "l", col = "blue", ylim = c(0,0.4))
lines(smws32_1mean$Group.1,smws32_1mean$smois60B, type = "l", col = "black", ylim = c(0,0.4))
legend("topright",inset = 0.05, legend=c("SM1-30A","SM1-30B","SM1-60A","SM1-60B"), col=c("red","orange","blue","black"), lty=1)}


{plot(density(smws32_1mean$smois30A), ylim = c(0,14), xlim = c(0,0.35), col = 'red', main = "Density of Observed Soil Moisture WS32 Station 1")
lines(density(smws32_1mean$smois30B), col = 'orange')
lines(density(smws32_1mean$smois60A), col = 'blue')
lines(density(smws32_1mean$smois60B), col = 'black')
legend("topright",inset = 0.05, legend=c("SM1-30A","SM1-30B","SM1-60A","SM1-60B"), col=c("red","orange","blue","black"), lty=1)}


{plot(smws32_2mean$Group.1,smws32_2mean$smois30A, type = "l", col = "red", ylim = c(0,0.4), xlab = "Date", ylab = "Soil Moisture", main = "Truncated Observed Soil Moisture WS32 Station 2")
lines(smws32_2mean$Group.1,smws32_2mean$smois30B, type = "l", col = "orange", ylim = c(0,0.4))
lines(smws32_2mean$Group.1,smws32_2mean$smois60A, type = "l", col = "blue", ylim = c(0,0.4))
lines(smws32_2mean$Group.1,smws32_2mean$smois60B, type = "l", col = "black", ylim = c(0,0.4))
legend("topright",inset = 0.05, legend=c("SM2-30A","SM2-30B","SM2-60A","SM2-60B"), col=c("red","orange","blue","black"), lty=1)}

##extra filtering for smws32_60a
smws32_2mean <- smws32_2mean %>%
  mutate(smois60A = replace(smois60A,Date >= "2017-11-26", NA ))

{plot(smws32_2mean$Group.1,smws32_2mean$smois30A, type = "l", col = "red", ylim = c(0,0.4), xlab = "Date", ylab = "Soil Moisture", main = "Truncated Observed Soil Moisture WS32 Station 2 Filtered")
lines(smws32_2mean$Group.1,smws32_2mean$smois30B, type = "l", col = "orange", ylim = c(0,0.4))
lines(smws32_2mean$Group.1,smws32_2mean$smois60A, type = "l", col = "blue", ylim = c(0,0.4))
lines(smws32_2mean$Group.1,smws32_2mean$smois60B, type = "l", col = "black", ylim = c(0,0.4))
legend("topright",inset = 0.05, legend=c("SM2-30A","SM2-30B","SM2-60A","SM2-60B"), col=c("red","orange","blue","black"), lty=1)}

{plot(smws32_3mean$Group.1,smws32_3mean$smois30A, type = "l", col = "red", ylim = c(0,0.4), xlab = "Date", ylab = "Soil Moisture", main = "Truncated Observed Soil Moisture WS32 Station 3")
lines(smws32_3mean$Group.1,smws32_3mean$smois30B, type = "l", col = "orange", ylim = c(0,0.4))
lines(smws32_3mean$Group.1,smws32_3mean$smois60A, type = "l", col = "blue", ylim = c(0,0.4))
lines(smws32_3mean$Group.1,smws32_3mean$smois60B, type = "l", col = "black", ylim = c(0,0.4))
legend("topright",inset = 0.05, legend=c("SM3-30A","SM3-30B","SM3-60A","SM3-60B"), col=c("red","orange","blue","black"), lty=1)}

soilmoisture30a<- data.frame(smws32_1mean$Date,smws32_1mean$smois30A, smws32_1mean$smois30B,smws32_1mean$smois60A,smws32_1mean$smois60B)
soilmoisture30b<- data.frame(smws32_2mean$Date,smws32_2mean$smois30A, smws32_2mean$smois30B,smws32_2mean$smois60A,smws32_2mean$smois60B)
soilmoisture30c<- data.frame(smws32_3mean$Date,smws32_3mean$smois30A,smws32_3mean$smois30B,smws32_3mean$smois60A,smws32_3mean$smois60B)


merged30a<- merge(soilmoisture30a,soilmoisture30b, by.x = "smws32_1mean.Date", by.y = "smws32_2mean.Date", all = FALSE)

merged30b<- merge(merged30a,soilmoisture30c, by.x = "smws32_1mean.Date", by.y = "smws32_3mean.Date", all = TRUE)

merged30c<- as.data.frame(rowMeans((merged30b[-1]), na.rm= TRUE))


mergedsm<- cbind(merged30b,merged30c)

colnames(mergedsm)<- c("Date","smois30site1a","smois30site1b","smois60site1a","smois60site1b","smois30site2a","smois30site2b","smois60site2a","smois60site2b","smois30site3a","smois30site3b","smois60site3a","smois60site3b","mergedsoilmoisture")

plot(mergedsm$Date, mergedsm$mergedsoilmoisture, type = "l", main = "Average WS32 Soil Moisture", xlab = "Date", ylab = "Merged Soil Moisture All Data")


plot(mergedsm)

## Calculate Calibration/Validation Split based on SM data

# range(mergedsm$Date)

daysofsmdata<- as.numeric(range(mergedsm$Date)[2] - range(mergedsm$Date)[1])

#70/30 split

Caldays<- round(0.7*daysofsmdata)
Valdays<- daysofsmdata-Caldays

Caldates<- as.Date(1)

Caldates[1]<- range(mergedsm$Date)[1]

Caldates[2]<- range(mergedsm$Date)[1]+Caldays

Valdates<- as.Date(1)

Valdates[1]<-  range(Caldates)[2]+1

Valdates[2]<- range(mergedsm$Date)[2]


```

Plot and Filter Observed Streamflow Data

Original Datasets are recorded as Water Year, We convert to calendar year

```{r Read and Prepare observed Streamflow data for WS32}
## import daily flow dataset
obsws32<- read.csv('C:/Users/Carlos/Desktop/ORISE/Streamflow Data/CW/Streamflow/Daily Streamflow Watershed 32/Daily Streamflow Watershed 32/daily_flow_ws32.csv', header = F) 

# dataset is recorded as water year, here we convert from water year and note that the water year for this landscape begins in November
## calendar year seems to be correct

obsws32$WYR <- as.numeric(obsws32$V1)
obsws32$Month <- as.numeric(obsws32$V2)
obsws32$Day <- as.numeric(obsws32$V3)
obsws32$flow <- as.numeric(obsws32$V4)

obsws32$CalendarYear<- ifelse((obsws32$Month=="12"|obsws32$Month=="11"),obsws32$WYR-1,obsws32$WYR)

obsws32$CalendarDate <- as.Date(with(obsws32,paste(CalendarYear,Month,Day,sep="-")),"%Y-%m-%d") 

##this removal of 0s may be reason for lag, 0s may be purposefully included in dataset
# instead create timeseries of date from start to end of timeseries and then merge
#obsws32<- obsws32[!(obsws32$flow=="0"),]

obsws32 <- drop_na(obsws32)

plot(obsws32$CalendarDate, obsws32$flow, type = "l", ylab = "Observed Discharge mm/d", xlab = "Date", main = "Observed Discharge WS32 Older Dataset")

obsws32_1<- read.csv('C:/Users/Carlos/Desktop/ORISE/Streamflow Data/CW/Streamflow/Daily Streamflow Watershed 32/Daily Streamflow Watershed 32/daily_flow_ws32_2017.csv', header = T)
obsws32_2<- read.csv('C:/Users/Carlos/Desktop/ORISE/Streamflow Data/CW/Streamflow/Daily Streamflow Watershed 32/Daily Streamflow Watershed 32/daily_flow_ws32_2018.csv', header = T)
obsws32_3<- read.csv('C:/Users/Carlos/Desktop/ORISE/Streamflow Data/CW/Streamflow/Daily Streamflow Watershed 32/Daily Streamflow Watershed 32/daily_flow_ws32_2019.csv', header = T)
obsws32_4<- read.csv('C:/Users/Carlos/Desktop/ORISE/Streamflow Data/CW/Streamflow/Daily Streamflow Watershed 32/Daily Streamflow Watershed 32/daily_flow_ws32_2020.csv', header = T)
obsws32_5<- read.csv('C:/Users/Carlos/Desktop/ORISE/Streamflow Data/CW/Streamflow/Daily Streamflow Watershed 32/Daily Streamflow Watershed 32/daily_flow_ws32_2021.csv', header = T)

obsws32b<- rbind(obsws32_1,obsws32_2,obsws32_3,obsws32_4,obsws32_5)

obsws32b$CalendarDate <- as.Date(with(obsws32b,paste(year,month,day,sep="-")),"%Y-%m-%d")

plot(obsws32b$CalendarDate,obsws32b$flow, type = "l", xlab = "Date", ylab = "Streamflow", main = "Observed Discharge WS32 Newer Datasets Merged")

dataset1   <- data.frame(Date=obsws32$CalendarDate,flow=obsws32$flow)
dataset2   <- data.frame(Date=obsws32b$CalendarDate,flow=obsws32b$flow)

fullset<- rbind(dataset1,dataset2)

### Streamflow at Coweeta logged as CSM
### conversion from EcohydRology project
## because we are converting from CSM we set watershed area to 1

fullset$discharge_mm<- ConvertFlowUnits(cfs = fullset$flow, WA=1, AREAunits = "mi2")

#{plot(fullset$Date,fullset$flow, type = "l", xlab = "Date", ylab = "Flow", main = "Streamflow WS32")
#lines(fullset$Date,fullset$discharge_mm, col = 'red')}

plot(fullset$Date,fullset$discharge_mm, type = "l", xlab = "Date", ylab = "Discharge mm/d", main = "Observed Discharge WS32 All Datasets Merged")

plot(fullset$Date,fullset$discharge_mm, type = "l", xlab = "Date", ylab = " Log Discharge mm/d", main = "Log of Observed Discharge WS32 All Datasets Merged", log = "y")

fullset$observedstreamflow<- fullset$discharge_mm

write.csv(fullset,"C:/Users/Carlos/Desktop/ORISE/Streamflow Data/CW/Streamflow/Daily Streamflow Watershed 32/Daily Streamflow Watershed 32/ObservedWS32.csv")

obsws32<- fullset

obsws32sm<- merge(obsws32,mergedsm, by = "Date")

#Caldates
#Valdates

obsws32cal <- obsws32[obsws32$Date >= Caldates[1] & obsws32$Date <= Caldates[2], ]
  
obsws32val <- obsws32[obsws32$Date >= Valdates[1] & obsws32$Date <= Valdates[2], ]
  
obsws32smcal <- obsws32sm[obsws32sm$Date >= Caldates[1] & obsws32sm$Date <= Caldates[2], ]

obsws32smval <- obsws32sm[obsws32sm$Date >= Valdates[1] & obsws32sm$Date <= Valdates[2], ]


```

Merge Observed and Simulated Data

```{r Merge Observed and Simulated Datasets}
## merge values instead of subsetting to match up with simulated dates
singleruntest$bd<- merge(singleruntest$bd,obsws32, by.x = "date", by.y = "Date", all = FALSE)

## merge soil moisture values but include all data
singleruntest$data <-merge(singleruntest$bd,obsws32sm, by.x = "date", by.y = "Date", all = TRUE)
```

Plot Observed and Simulated Data, Plot RHESSys Outputs

```{r Plot Observed and Simulated Datasets}
## Plot Hydrograph comparing modeled and observed streamflow
{hydrograph(input=singleruntest$bd, streamflow=singleruntest$bd$observedstreamflow, streamflow2 = singleruntest$bd$streamflow, timeSeries = singleruntest$bd$date, precip = singleruntest$bd$streamflow,
           P.units = "mm", S.units = "mm normalized by basin area", S1.col = 'Blue', S2.col = 'Red')

legend("topleft",inset = .2, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("blue","red"), lty=1:2)}

{plot(singleruntest$data$date,singleruntest$data$observedstreamflow.x, type = "l", xlab = "Date", ylab = "Streamflow", main = "Predicted vs Observed Streamflow")
lines(singleruntest$data$date, singleruntest$data$streamflow, col = 'RED')
legend("topright",inset = 0, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("black","red"), lty=1:1)}

{plot(singleruntest$data$date,singleruntest$data$observedstreamflow.x, type = "l", xlab = "Date", ylab = "Streamflow", main = "Predicted vs Observed Log Streamflow", log = "y")
lines(singleruntest$data$date, singleruntest$data$streamflow, col = 'RED')
legend("topright",inset = 0, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("black","red"), lty=1:1)}

predictedvsobservedstreamlm<- lm(observedstreamflow~streamflow, data = singleruntest$bd)

{plot(singleruntest$bd$observedstreamflow,singleruntest$bd$streamflow, xlab = "Observed", ylab = "Predicted", main = "Predicted vs Observed Streamflow", xlim = c(0,55), ylim = c(0,55))
abline(a=0, b=1, col = 'RED', lty = 2, lwd = 2)
legend("right",inset = 0.01, legend = paste("R2 =",format(summary(predictedvsobservedstreamlm)$r.squared,digits=3)))}

{plot(singleruntest$data$date,(singleruntest$data$rz_storage/singleruntest$data$rootdepth), type = "l", ylim = c(0,0.35), xlab = "Date", ylab = "RZ_Storage/Rootdepth", main = "Predicted vs Observed Basin Scale Soil Moisture")
lines(singleruntest$data$date, singleruntest$data$mergedsoilmoisture, col = 'RED')
legend("topright",inset = 0, legend=c("Observed Soil Moisture","Predicted Soil Moisture"), col=c("black","red"), lty=1:1)}

predictedvsobservedsoillm<- lm((rz_storage/rootdepth)~mergedsoilmoisture, data = singleruntest$data)

{plot((singleruntest$data$rz_storage/singleruntest$data$rootdepth),singleruntest$data$mergedsoilmoisture, xlab = "Observed", ylab = "Predicted", main = "Predicted vs Observed Basin Scale Soil Moisture", xlim = c(0.05,0.4), ylim = c(0.05,0.4))
abline(a=0, b=1, col = 'RED', lty = 2, lwd = 2)
legend("right",inset = 0.01, legend = paste("R2 =",format(summary(predictedvsobservedsoillm)$r.squared,digits=3)))}

## Plot other model outputs

par(mfrow=c(5,1), mar = c(2,5,4,2))

plot(singleruntest$bd$date,singleruntest$bd$tmin, type = "l", col = 'BLUE', ylim = c(-15,30), ylab = "Temperature", xlab = "Date")
lines(singleruntest$bd$date,singleruntest$bd$tmax, type = "l", col = 'RED')
plot(singleruntest$bd$date,singleruntest$bd$precip, type = "h", ylab = "Precipitation", xlab = "Date")
plot(singleruntest$bd$date,singleruntest$bd$streamflow, type = "l", ylab = "Streamflow", xlab = "Date", col = 'blue')
plot(singleruntest$bd$date,singleruntest$bd$baseflow, type = "l", ylab = "Baseflow", xlab = "Date", col = 'brown')
plot(singleruntest$bd$date,singleruntest$bd$rz_storage, type = "l", ylab = "RZ Storage", xlab = "Date", col = 'dark green')
plot(singleruntest$bd$date,singleruntest$bd$psn ,type = "l", ylab = "PSN", xlab = "Date")
plot(singleruntest$bd$date,singleruntest$bd$et, type = "l", ylab = "Evaoptranspiration", xlab = "Date")
plot(singleruntest$bd$date,singleruntest$bd$pet, type = "l", ylab = "PET", xlab = "Date")
plot(singleruntest$bd$date,singleruntest$bd$gw.Qout, type = "l", ylab = "Q out", xlab = "Date")
plot(singleruntest$bd$date,singleruntest$bd$gw.storage, type = "l", ylab = "GW Storage", xlab = "Date")

par(mfrow=c(1,1))

### will only plot in growth mode , used to check that vegetation is initialized properly ##
plot(singleruntest$bdg$date, singleruntest$bdg$lai, type = "l", main = "LAI", xlab = "Date")
plot(singleruntest$bdg$date, singleruntest$bdg$soilc, type = "l", main = "Soil Carbon", xlab = "Date")


## plot cal/val sets

{plot(singleruntest$data$date,(singleruntest$data$rz_storage/singleruntest$data$rootdepth), type = "l", ylim = c(0,0.35),xlim = c(obsws32smcal$Date[1],obsws32smval$Date[length(obsws32smval$Date)]), xlab = "Date", ylab = "RZ_Storage/Rootdepth", main = "Predicted vs Observed Basin Scale Soil Moisture")
lines(obsws32smcal$Date,obsws32smcal$mergedsoilmoisture, col = "BLUE")
lines(obsws32smval$Date,obsws32smval$mergedsoilmoisture, col = "RED")
legend("topright",inset = 0, legend=c("Predicted Soil Moisture","Observed Calibration Soil Moisture", "Observed Validation Soil Moisture"), col=c("black","blue","red"), lty=c(1,1,1))}

{plot(singleruntest$data$date,singleruntest$data$streamflow, type = "l", xlab = "Date", ylab = "Streamflow", main = "Predicted vs Observed Basin Scale Streamflow",xlim = c(obsws32smcal$Date[1],obsws32smval$Date[length(obsws32smval$Date)]))
lines(obsws32cal$Date,obsws32cal$observedstreamflow, col = "BLUE")
lines(obsws32val$Date,obsws32val$observedstreamflow, col = "RED")
legend("topright",inset = 0, legend=c("Predicted Streamflow","Observed Calibration Streamflow", "Observed Validation Streamflow"), col=c("black","blue","red"), lty=c(1,1,1))}
```

Testing Precip input vs model precip

```{r eval=FALSE, include=FALSE}
str(daymet_data$data)

daymetdate <- as.Date(paste(daymet_data$data$year,daymet_data$data$yday, sep = "-"), format = "%Y - %j")

str(daymetdate)

daymet_data$data$appendeddate<- daymetdate

xlim=  c(as.Date(singleruntest$bd$date[1]),as.Date(singleruntest$bd$date[length(singleruntest$bd$date)]))

plot(daymet_data$data$appendeddate,daymet_data$data$prcp..mm.day., type = 'h')



{plot(singleruntest$bd$date, singleruntest$bd$precip, type = 'h')


lines(daymet_data$data$appendeddate,daymet_data$data$prcp..mm.day., type = 'h', col = 'red')}


## lag likely caused by mismatch in in put precip data and model input precip data

## attempt to remedy this by creating date vector and appending precip values, replace blanks with na or 0


{plot(singleruntest$bd$date, singleruntest$bd$precip, type = 'h')


lines(fulldaymetprecip$Dates,fulldaymetprecip$prcp..mm.day., type = 'h', col = 'red')}


```

Spatial Data Display

```{r Display Spatial Inputs and Simulated Soil Moisture, fig.height=10, fig.width=14}
setwd(system.file("extdata/", package = "RHESSysIOinR"))

# Original input maps have been cropped before processing in R, without cropping the RHESSYs preparation in the R environment will not function properly, below are the input maps used by R
ws32<- raster("grassexport/cwt_ws32/basin_ws32.tif")
patches<- raster("grassexport/cwt_ws32/patch.tif")
acc10<- raster("grassexport/cwt_ws32/acc10.tif")
aspect10<- raster("grassexport/cwt_ws32/aspect10.tif")
#bt1000<- raster("C:/Users/Carlos/Documents/R/win-library/4.0/RHESSysIOinR/extdata/rasters/cwt_ws32/ws32/b.t1000.tif")
dem10<- raster("grassexport/cwt_ws32/dem10.tif")
dem10f<- raster("grassexport/cwt_ws32/dem10f.tif")
dir10<- raster("grassexport/cwt_ws32/dir10.tif")
drain10<- raster("grassexport/cwt_ws32/drain10.tif")
#ht1000<- raster("C:/Users/Carlos/Documents/R/win-library/4.0/RHESSysIOinR/extdata/rasters/cwt_ws32/ws32/h.t1000.tif")
hillslope<- raster("grassexport/cwt_ws32/hillslope.tif")
roads<- brick("grassexport/cwt_ws32/roads.tif")
#shade10<- raster("C:/Users/Carlos/Documents/R/win-library/4.0/RHESSysIOinR/extdata/rasters/cwt_ws32/ws32/shade10.tif")
slope10<- raster("grassexport/cwt_ws32/slope10.tif")
streams<- raster("grassexport/cwt_ws32/streams.tif")
topidx10<- raster("grassexport/cwt_ws32/topidx10_100.tif")
#xmap<- raster("C:/Users/Carlos/Documents/R/win-library/4.0/RHESSysIOinR/extdata/rasters/cwt_ws32/ws32/xmap.tif")
#ymap<- raster("C:/Users/Carlos/Documents/R/win-library/4.0/RHESSysIOinR/extdata/rasters/cwt_ws32/ws32/ymap.tif")

soilstatic<- raster("grassexport/cwt_ws32/ssurgosoil.tif")

reclass_df <- c(0,256,9)
reclass_static <- matrix(reclass_df, ncol = 3, byrow = TRUE)
soilstaticmap<- reclassify(soilstatic, reclass_static)


soilssurgo<- raster("grassexport/cwt_ws32/ssurgosoil.tif")
soildsm<- raster("grassexport/cwt_ws32/dsmsoil.tif")
veg<- raster("grassexport/cwt_ws32/nlcdveg.tif")




plot(ws32, main ="ws32")
plot(patches, main = "patches")
plot(acc10, main = "acc10")
plot(aspect10, main = "aspect10")
#levelplot(bt1000, col.regions = brewer.pal(name='Spectral', n = 11),at=seq(0,6500,1))
#plot(bt1000, main = "bt1000")
plot(dem10, main = "dem10")
plot(dem10f, main = "dem10f")
plot(dir10, main = "dir10")
plot(drain10, main = "drain10")
#plot(ht1000, main = "ht1000")
plot(hillslope, main = "hillslope")
plot(roads, main = "roads")
#plot(shade10, main = "shade10")
plot(slope10, main = "slope10")
plot(streams, main = "streams")
plot(topidx10, main = "topidx10")
#plot(xmap, main = "xmap")
#plot(ymap, main = "ymap")

plot(soilstaticmap, main = "Static Soil Input", zlim = c(0,26))
plot(soilssurgo, main = "SSURGO Soil Input", zlim = c(0,26))
plot(soildsm, main = "RSS Soil Input", zlim = c(0,26))

plot(veg, main = "NLCD Veg Input")



```

New Soil Map Figure

```{r}

## plot 3 rasters with common legend, legend should only be integers shown in rasters




```

Quick map creation for WS7 soil moisture data display

```{r}

ws7demcrop <- crop(resampleddem,x[27,])
ws7demcrop <- mask(ws7demcrop,x[27,])
plot(ws7demcrop)



Observedws7SMLocationsnt <- read_sf("C:/Users/Carlos/Desktop/ORISE/Soil Moisture Data/CW/knb-lter-cwt.1305.19/1305.kml")
Observedws7SMLocations <- st_transform(Observedws7SMLocationsnt, crs(dem10))

Newsoilmoisturelocationsnt<- read_sf(newsmlocations)
Newsoilmoisturelocations<- st_transform(Newsoilmoisturelocationsnt, crs(dem10))

colorramp<- viridis(1028)

{plot(ws7demcrop, col = colorramp, main = "Coweeta Observed Soil Moisture Locations WS32", legend.args=list(text="Elevation(m)", side = 3, line = 2))
points(c(Observedws7SMLocations[[3]][[3]][1],Observedws7SMLocations[[3]][[4]][1],Observedws7SMLocations[[3]][[5]][1]), c(Observedws7SMLocations[[3]][[3]][2],Observedws7SMLocations[[3]][[4]][2],Observedws7SMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", lwd = 1)
points(st_coordinates(Newsoilmoisturelocations), pch =21, col = "black", bg = "green", lwd = 1)
legend("topright", legend = c("Legacy","New"), pch = 20, col= c("red","green"), cex = 1.2)
}

```

Show Observed Soil Moisture Locations

```{r Map of Locations of Observed Soil Moisture, fig.height=10, fig.width=10}

ObservedSMLocationsnt <- read_sf("C:/Users/Carlos/Desktop/ORISE/Soil Moisture Data/CW/knb-lter-cwt.1308.19/1308.kml")

ObservedSMLocations <- st_transform(ObservedSMLocationsnt, crs(dem10))


Newsoilmoisturelocationsnt<- read_sf(newsmlocations)

Newsoilmoisturelocations<- st_transform(Newsoilmoisturelocationsnt, crs(dem10))

colorramp<- viridis(1028)

{plot(dem10, col = colorramp, main = "Coweeta Observed Soil Moisture Locations")
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", lwd = 1)

}

 {plot(dem10, col = colorramp, main = "Coweeta Observed Soil Moisture Locations WS32", legend.args=list(text="Elevation(m)", side = 3, line = 2))
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", lwd = 1)
points(st_coordinates(Newsoilmoisturelocations), pch =21, col = "black", bg = "green", lwd = 1)
legend("topright", legend = c("Legacy","New"), pch = 20, col= c("red","green"), cex = 1.2)
}

ObservedSMLocations$Name[3]
ObservedSMLocations[[3]][[3]]

ObservedSMLocations$Name[4]
ObservedSMLocations[[3]][[4]]

ObservedSMLocations$Name[5]
ObservedSMLocations[[3]][[5]]

matrix(c(ObservedSMLocations$Name[3],ObservedSMLocations$Name[4],ObservedSMLocations$Name[5],ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1],ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), nrow = 3, ncol = 3)

library(mapview)

Coweeta <- st_read(watershedshapefile)

mapview(Coweeta, label = Coweeta$WS, alpha.regions = 0.1, alpha = 1) +
  mapview(ObservedSMLocations[3:5,]) 



par(mfrow=c(1,2),mar=c(2, 3, 2, 5))
 {plot(dem10, col = colorramp, main = "WS32", legend.args=list(text="          Elevation(m)", side = 3, line = 2, cex = 0.8))
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", lwd = 1)
points(st_coordinates(Newsoilmoisturelocations), pch =21, col = "black", bg = "green", lwd = 1)
legend("topright", legend = c("Legacy","New"), pch = 20, col= c("red","green"), cex = 1.2)
}

{plot(ws7demcrop, col = colorramp, main = "WS7", legend.args=list(text="          Elevation(m)", side = 3, line = 2, cex = 0.8))
points(c(Observedws7SMLocations[[3]][[3]][1],Observedws7SMLocations[[3]][[4]][1],Observedws7SMLocations[[3]][[5]][1]), c(Observedws7SMLocations[[3]][[3]][2],Observedws7SMLocations[[3]][[4]][2],Observedws7SMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", lwd = 1)
points(st_coordinates(Newsoilmoisturelocations), pch =21, col = "black", bg = "green", lwd = 1)
legend("topright", legend = c("Legacy","New"), pch = 20, col= c("red","green"), cex = 1.2)
}
par(mfrow=c(1,1))
```

Display Observed and Simulated Soil Moisture

```{r Display Spatial Outputs and Simulated Soil Moisture, fig.height=10, fig.width=14}
## Extract values for single date
displayday <- singleruntest$pd[which(singleruntest$pd$date=="2018-10-21")]

## reclassify all patches to na and then reclassify to model output values
reclass_all<- c(-2147483648, 2147483647,NA)
reclass_allm<- matrix(reclass_all, ncol = 3, byrow = TRUE)
displaydaypatches<- reclassify(patches,reclass_allm)

displayday$calculatedrzsm <- displayday$rz_storage/displayday$root.depth

reclass_displayday <- cbind(displayday$patchID,displayday$calculatedrzsm)
reclass_displayday <- as.matrix(reclass_displayday)
displaydaypatches<- reclassify(patches,reclass_displayday)

## Plot Spatial Data Output for RZ Storage
#plot(displaydaypatches, xlim = c(280900,282500), ylim = c(4870000,4872000))

{plot(mask(displaydaypatches,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600))
title("CW WS32 RZ Soil Moisture Prediction for 1 day", line = -2)
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", cex = 2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}


reclass_displayday <- cbind(displayday$patchID,displayday$root.depth)
reclass_displayday <- as.matrix(reclass_displayday)
displaydaypatches2<- reclassify(patches,reclass_displayday)

{plot(mask(displaydaypatches2,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600))
title("CW WS32 root.depth Prediction for 1 day", line = -2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}


reclass_displayday <- cbind(displayday$patchID,displayday$rz_storage)
reclass_displayday <- as.matrix(reclass_displayday)
displaydaypatches3<- reclassify(patches,reclass_displayday)

{plot(mask(displaydaypatches3,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600))
title("CW WS32 rz_storage Prediction for 1 day", line = -2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}

reclass_displayday <- cbind(displayday$patchID,displayday$sat_def)
reclass_displayday <- as.matrix(reclass_displayday)
displaydaypatches4<- reclassify(patches,reclass_displayday)

{plot(mask(displaydaypatches4,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600))
title("CW WS32 saturation deficit Prediction for 1 day", line = -2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}



reclass_displayday <- cbind(displayday$patchID,displayday$rz_field_capacity/1000)
reclass_displayday <- as.matrix(reclass_displayday)
displaydaypatches5<- reclassify(patches,reclass_displayday)

{plot(mask(displaydaypatches5,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600))
title("CW WS32 RZ Field Capacity for 1 day", line = -2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}



## Plot Hydrograph
{hydrograph(input=singleruntest$bd, streamflow=singleruntest$bd$observedstreamflow, streamflow2 = singleruntest$bd$streamflow, timeSeries = singleruntest$bd$date, precip = singleruntest$bd$streamflow,
           P.units = "mm", S.units = "mm normalized by basin area", S1.col = 'Blue', S2.col = 'Red')
legend("topleft",inset = .2, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("blue","red"), lty=1:2)}

### end show patch map

patchnumbers<- raster::extract(patches,matrix(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1],ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), nrow = 3, ncol = 2))


ObserveSoilMoisturePatches <- matrix(c(ObservedSMLocations$Name[3],ObservedSMLocations$Name[4],ObservedSMLocations$Name[5],ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1],ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2],patchnumbers), nrow = 3, ncol = 4)


## Extract values for a single patch, select patch ID
ObserveSoilMoisturePatches[1,4]
displaypatch<- singleruntest$pd[which(singleruntest$pd$patchID==ObserveSoilMoisturePatches[1,4])]
ObserveSoilMoisturePatches[2,4]
displaypatch2<- singleruntest$pd[which(singleruntest$pd$patchID==ObserveSoilMoisturePatches[2,4])]
ObserveSoilMoisturePatches[3,4]
displaypatch3<- singleruntest$pd[which(singleruntest$pd$patchID==ObserveSoilMoisturePatches[3,4])]

plot(displaypatch$date,(displaypatch$rz_storage/displaypatch$root.depth), type = "l", xlab = "Date", ylab = "RZ Storage", main = 'CW WS27 More Detailed RZ Storage Patch #147322', ylim = c(0,.4))

{plot(smws32_1mean$Group.1,smws32_1mean$smois30A, type = "l", ylim = c(0,.4), col = 'darkorange', xlim=as.Date(c("2016-10-1","2019-10-1")), main = "CW WS32 More Detailed Soil Moisture vs Patches",
     xlab = "Date", ylab = "Soil Moisture mm")
lines(smws32_2mean$Group.1,smws32_2mean$smois30A,type = "l", col = 'darkred')
lines(smws32_3mean$Group.1,smws32_3mean$smois30A,type = "l", col = 'blue')
lines(displaypatch$date,(displaypatch$rz_storage/displaypatch$root.depth), type = "l", xlab = "Date", ylab = "RZ Storage", col = 'red', lty = 2)
lines(displaypatch2$date,(displaypatch2$rz_storage/displaypatch2$root.depth), type = "l", xlab = "Date", ylab = "RZ Storage", col = 'green', lty = 2)
lines(displaypatch3$date,(displaypatch3$rz_storage/displaypatch3$root.depth), type = "l", xlab = "Date", ylab = "RZ Storage", col = 'black', lty = 2)

legend("bottomleft",inset = .01, legend=c("Observed Patch 1","Predicted Patch 1","Observed Patch 2","Predicted Patch 2","Observed Patch 3","Predicted Patch 3"), col=c("darkorange", "red","darkred","green","blue","black"), lty=c(1,2,1,2,1,2))}

{plot(smws32_2mean$Group.1,smws32_2mean$smois30A, type = "l", ylim = c(0,0.4), col = 'BLUE', xlim=as.Date(c("2016-10-1","2019-10-1")), main = "CW WS32 More Detailed Soil Moisture vs Patch #154914",
     xlab = "Date", ylab = "Soil Moisture mm")
lines(displaypatch$date,(displaypatch$rz_storage/displaypatch$root.depth), type = "l", xlab = "Date", ylab = "RZ Storage", main = 'CW WS27 More Detailed RZ Storage Patch #154914', col = 'red')
legend("bottomleft",inset = .01, legend=c("Observed Soil Moisture","Predicted Soil Moisture"), col=c("blue","red"), lty=1:1)}


#
#obsws32cal <- obsws32[obsws32$Date >= Caldates[1] & obsws32$Date <= Caldates[2], ]
#obsws32val <- obsws32[obsws32$Date >= Valdates[1] & obsws32$Date <= Valdates[2], ]
#obsws32smcal <- obsws32sm[obsws32sm$Date >= Caldates[1] & obsws32sm$Date <= Caldates[2], ]
#obsws32smval <- obsws32sm[obsws32sm$Date >= Valdates[1] & obsws32sm$Date <= Valdates[2], ]

head(obsws32cal)
head(obsws32val)
head(obsws32smcal)
head(obsws32smval)

#subset Validation range based on Val Dates set by available SM data

validationsubset <- singleruntest$bd[singleruntest$bd$date >= Valdates[1] & singleruntest$bd$date <= Valdates[2], ]

## Fit tests for streamflow

NSE(validationsubset$streamflow,validationsubset$observedstreamflow)

NSE(validationsubset$streamflow,validationsubset$observedstreamflow, FUN=log, epsilon = "Pushpalatha2012", na.rm=TRUE)

nse_value <- NSE(log(validationsubset$streamflow + 1), log(validationsubset$observedstreamflow + 1), na.rm = TRUE)


 KGE(validationsubset$streamflow,validationsubset$observedstreamflow)

plot(validationsubset$streamflow~validationsubset$date, type = "l", col = 'red')
lines(validationsubset$observedstreamflow~validationsubset$date)

# Plot Observed and Predicted Streamflow

{plot(validationsubset$date,validationsubset$streamflow, type = 'l', lty = 2, col = 'RED', main = "Streamflow")
lines(validationsubset$date,validationsubset$observedstreamflow, type = 'l', col = 'BLACK')
legend("topright",inset = .1, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("black","red"), lty=1:2)}


{plot(singleruntest$bd$date,singleruntest$bd$streamflow, type = 'l', lty = 2, col = 'RED', main = "Streamflow")
lines(singleruntest$bd$date,singleruntest$bd$observedstreamflow, type = 'l', col = 'BLACK')
legend("topright",inset = .1, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("black","red"), lty=1:2)}

#Plot Model RZ SM outputs for patch
{plot(displaypatch$date,(displaypatch$rz_storage/displaypatch$root.depth), type = "l",ylim = c(0,0.50), ylab = "Root Zone Storage (mm/m) ", xlab = "Date", main = 'Root Zone Display Patch')
lines(displaypatch$date,(displaypatch$rz_field_capacity/displaypatch$root.depth), type = "l", col = "blue")
lines(displaypatch$date,(displaypatch$rz_wilting_point/displaypatch$root.depth), type = "l", col = "red")
legend("bottomleft",inset = .1, legend=c("Predicted RZ Storage","RZ Field Capacity","RZ Wilting Point"), col=c("black","blue","red"), lty=1:1)}

```

Setup RHESSys Calibration, CLHS used to reduce amount of samples processed

The model calibrates over the following parameters.

M - Decay of hydraulic conductivity with depth
K - Hydraulic conductivity at the surface
Sd - soil depth
Mv - Vertical decay of hydraulic conductivity with depth
Kv - Vertical hydraulic conductivity at the surface
GW1 - Saturated to Groundwater Coefficient
GW2 - Groundwater Loss Coefficient


Parameter & Typical Range from RHESSys Wiki

M - .01 - 20
K - 1 - 600
GW1 -  .001 - .3
GW2 -  .01 - .9

" In order to generate an adequate sample across the full range for each parameter, values from .001 - .01, values from .01 - 1, and values over 1 should be generated separately. The m and K parameters are multipliers on the initial values set for m and K (values assigned to the m and K maps)." - Taken from RHESSys Wiki

Additional Calibration Parameters are available natively although they are not as well documented

pa - multiplier to scale the pore size index
po - multiplier to scale the psi air entry 

vseng1 - multiplies specific leaf areas
vseng2 - multiplies the ratio of shaded to sunlit leaf area
vseng3 - Multiplier used only with the Dickenson algorithm of carbon allocation (set with the epc.allocation_flag variable in the vegetation definition file). It changes the allocation of net photosynthate sensitivity based on the current LAI. If not using the Dickenson strategy of carbon allocation (i.e. using Waring or default Constant strategies), set third value to 1.0. (i.e. -vgsen 1.0 2.0 1.0)

```{r RHESSys Calibration Parameter Setup}
setwd(system.file("extdata/", package = "RHESSysIOinR"))
# number of samples for full data space
fs <- 10000
# number of samples to calibrate over, 100 samples take approx 40 mins in base R and 1 hour in rmarkdown
n <- 200
# create data frame
d <- data.frame(
  m = runif(fs, min=0.5, max=5),
  k = runif(fs, min=0.5, max=60),
  soil_dep = runif(fs, min=0.1, max=0.5),
  m_v = runif(fs, min=0.5, max=15),
  k_v = runif(fs, min=0.5, max=15),
  gw1 = runif(fs, min=0.1, max=0.3),
  gw2 = runif(fs, min=0.1, max=0.6),
  pa = runif(fs, min=0.1, max=1.0),
  po = runif(fs, min=1.0, max=2.0),
  vgseng1 = runif(fs, min=0.1, max=2.0),
  vgseng2 = runif(fs, min=0.1, max=2.0),
  vgseng3 = runif(fs, min=0.1, max=2.0))
# marginal distributions, for analysis
m <- melt(d)
bwplot(variable ~ value, data = m, par.settings = tactile.theme(), main = "distribution of calibration parameters before clhs subsetting")
# cLHS subset
s <- clhs(d, size = n, simple = TRUE, use.cpp = TRUE)
# combine full dataset + subset
g <- make.groups(full = d, cLHS = d[s, ])
# create new list
params<- d[s, ]

params[1:5,]

## Quick and dirty way to include "uncalibrated" result to test against, groundwater model still included for now, unsure of what to do with parameters for gw
## params[1,] = c(1,1,1,1,1,0,0)
## did not produce significantly different result

#write param table to specific text file if file does not exist
## if name is not changed then old table is used
# paramtablename = "out/cwparamtable021723.txt" 

####WORKING

### WORKING

### WORKING
getwd()


##
##UNCOMMENT TO WRITE NEW PARAMS
## write.table(params, file = "out/cwparamtable091923.txt")
###

### writes new params table with todays date to a text file
#write.table(params, file = paste("out/cwparamtable",format(Sys.Date(),"%m%d%y"),".txt",sep = ""))

## reads in specific params file, used for keeping input params constant for analysis
## do not rewrite file if it exits

#{if (file.exists("out/cwparamtable102522.txt"))
#   print("text")}


 #params <- read.table(file = "out/cwparamtable102522.txt")
#params <- read.table(file = "out/cwparamtable032823.txt")
params <- read.table(file = "out/cwparamtable091923.txt")

# prepare RHESSys for run
params<- as.data.frame(params)


input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32dsm.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32dsm",
  flowtable = "CWWS32dsm1.flow",
  start = "2013 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32",
  commandline_options = c("-b"))


#commandline_options = c("-b -p 1 128 154914 154914 ")) <- Patch Specific Output
  
## must incorporate single patch output or local patch output for the purposes of calibration
## make sure to run calibration with no modifiers or 1 for everything except gw1 and gw2
## must refine calibration to do multiple steps, first gw1 gw2, then other variables
## multi point calibration and validation

input_tec_data = IOin_tec_std(start = "2015 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = c("defs/lu_undev.def","defs/lu_agriculture.def","defs/lu_raingarden.def","defs/lu_urban.def"),
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")
 
```
 
Run RHESSys n times sequentially

# NO LONGER USED

```{r RHESSys Sequential Calibration, eval=FALSE, include=FALSE}
start_time = Sys.time()

for(i in 1:n) {
 
stdpars<- IOin_std_pars(
  m = params[i,]$m,
  k = params[i,]$k,
  soil_dep= params[i,]$soil_dep,
  m_v = params[i,]$m_v,
  k_v = params[i,]$k_v,
  gw1 = params[i,]$gw1,
  gw2 = params[i,]$gw2,
  pa = params[i,]$pa,
  po = params[i,]$po,
  vgseng1 = params[i,]$vgseng1,
  vgseng2 = params[i,]$vgseng2,
  vgseng3 = params[i,]$vgseng3)

run_rhessys_single(input_rhessys = input_rhessys,
                   hdr_files = input_hdr,
                   tec_data = input_tec_data,
                   std_pars = stdpars,
                   runID = i)} 

end_time = Sys.time()

end_time - start_time

```

Run RHESSys in Parallel using the foreach package, leaving 4 cores available for other tasks

Takes about 1 hour for 100 runs at 10x10m Daily WS32.

# NO LONGER USED

```{r Run RHESSYS in Parallel using foreach, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:n, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = params[i,]$m,
                            k = params[i,]$k,
                            soil_dep= params[i,]$soil_dep,
                            m_v = params[i,]$m_v,
                            k_v = params[i,]$k_v,
                            gw1 = params[i,]$gw1,
                            gw2 = params[i,]$gw2,
                            pa = params[i,]$pa,
                            po = params[i,]$po,
                            vgseng1 = params[i,]$vgseng1,
                            vgseng2 = params[i,]$vgseng2,
                            vgseng3 = params[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

Prepare Static Inputs

```{r Static }
# prepare RHESSys for run
params<- as.data.frame(params)

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32static.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32static",
  flowtable = "CWWS32static1.flow",
  start = "2013 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32static",
  commandline_options = c("-b"))

#commandline_options = c("-b -p 1 128 154914 154914 ")) <- Patch Specific Output
  
## must incorporate single patch output or local patch output for the purposes of calibration
## make sure to run calibration with no modifiers or 1 for everything except gw1 and gw2
## must refine calibration to do multiple steps, first gw1 gw2, then other variables
## multi point calibration and validation

input_tec_data = IOin_tec_std(start = "2015 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = c("defs/lu_undev.def","defs/lu_agriculture.def","defs/lu_raingarden.def","defs/lu_urban.def"),
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")
 
```
# Modify for MCMC
Run RHESSys Calibration with Static Maps

```{r Run RHESSYS in Parallel using foreach Static, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:n, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = params[i,]$m,
                            k = params[i,]$k,
                            soil_dep= params[i,]$soil_dep,
                            m_v = params[i,]$m_v,
                            k_v = params[i,]$k_v,
                            gw1 = params[i,]$gw1,
                            gw2 = params[i,]$gw2,
                            pa = params[i,]$pa,
                            po = params[i,]$po,
                            vgseng1 = params[i,]$vgseng1,
                            vgseng2 = params[i,]$vgseng2,
                            vgseng3 = params[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

Prepare SSURGO Inputs

```{r SSURGO}
# prepare RHESSys for run
params<- as.data.frame(params)

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32ssurgo.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32ssurgo",
  flowtable = "CWWS32ssurgo1.flow",
  start = "2013 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32ssurgo",
  commandline_options = c("-b"))

#commandline_options = c("-b -p 1 128 154914 154914 ")) <- Patch Specific Output
  
## must incorporate single patch output or local patch output for the purposes of calibration
## make sure to run calibration with no modifiers or 1 for everything except gw1 and gw2
## must refine calibration to do multiple steps, first gw1 gw2, then other variables
## multi point calibration and validation

input_tec_data = IOin_tec_std(start = "2015 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = c("defs/lu_undev.def","defs/lu_agriculture.def","defs/lu_raingarden.def","defs/lu_urban.def"),
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")
 
```
# Modify for MCMC
Run RHESSys with SSURGO Maps

```{r Run RHESSYS in Parallel using foreach SSURGO, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:n, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = params[i,]$m,
                            k = params[i,]$k,
                            soil_dep= params[i,]$soil_dep,
                            m_v = params[i,]$m_v,
                            k_v = params[i,]$k_v,
                            gw1 = params[i,]$gw1,
                            gw2 = params[i,]$gw2,
                            pa = params[i,]$pa,
                            po = params[i,]$po,
                            vgseng1 = params[i,]$vgseng1,
                            vgseng2 = params[i,]$vgseng2,
                            vgseng3 = params[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

Prepare DSM Inputs

```{r DSM}
# prepare RHESSys for run
params<- as.data.frame(params)

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32dsm.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32dsm",
  flowtable = "CWWS32dsm1.flow",
  start = "2013 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32dsm",
  commandline_options = c("-b"))

#commandline_options = c("-b -p 1 128 154914 154914 ")) <- Patch Specific Output

input_tec_data = IOin_tec_std(start = "2015 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = c("defs/lu_undev.def","defs/lu_agriculture.def","defs/lu_raingarden.def","defs/lu_urban.def"),
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")
 
```
# Modify for MCMC
## must refine calibration to do multiple steps, first gw1 gw2, then other variables
## multi point calibration and validation

Run RHESSys with RSS Maps

```{r Run RHESSYS in Parallel using foreach DSM, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:n, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = params[i,]$m,
                            k = params[i,]$k,
                            soil_dep= params[i,]$soil_dep,
                            m_v = params[i,]$m_v,
                            k_v = params[i,]$k_v,
                            gw1 = params[i,]$gw1,
                            gw2 = params[i,]$gw2,
                            pa = params[i,]$pa,
                            po = params[i,]$po,
                            vgseng1 = params[i,]$vgseng1,
                            vgseng2 = params[i,]$vgseng2,
                            vgseng3 = params[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

Read in RHESSys Calibration Outputs and Plot

Calibration is performed using GLUE methodology and Nash-Sutcliffe Model Efficiency (NSE), Log-Normal Nash-Sutcliffe Model Efficiency (lnNSE), and Kling-Gupta Efficiency (KGE).

```{r Read in RHESSys Calibration Outputs and Plot, fig.height=9, fig.width=14, paged.print=TRUE}
 
setwd(system.file("extdata/", package = "RHESSysIOinR"))


testoutput<- readin_rhessys_output("out/cwws32_run200")


# Read in RHESSys Calibration runs
for(i in 1:n) { assign(paste0("cwws32_run",i), readin_rhessys_output(paste0("out/cwws32_run",i)))}

#Prepare observed Streamflow data
obsws32$Date<- as.Date(obsws32$Date)

## plot observed data for period of record and calibration/validation periods as defined by SM data
{plot(obsws32$Date,obsws32$discharge_mm, type = 'l', xlim=c(as.Date(input_rhessys$start_date, "%Y%m%d"),as.Date(input_rhessys$end_date, "%Y%m%d")),ylab = "Observed Discharge mm/d", xlab = "Date", main = "Observed Streamflow Discharge for period of time model is run")
abline(v=as.Date(Caldates[1]), col = 'red', lwd = 2, lty = 2)
abline(v=as.Date(Caldates[2]), col = 'red', lwd = 2, lty = 2)
abline(v=as.Date(Valdates[1]), col = 'blue', lwd = 2, lty = 5)
abline(v=as.Date(Valdates[2]), col = 'blue', lwd = 2, lty = 5)
legend("topright",inset = 0.05, legend=c("Calibration","Validation"), col=c("red","blue"), lty=1)}



##merge calibration runs with observed so dates match up, instead of subsetting 
for(i in 1:n) { assign(paste0("simmerge",i), merge(obsws32,eval(parse(text = paste0("cwws32_run",i,"$bd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("calsubset",i),eval(parse(text = paste0("simmerge",i)))[eval(parse(text = paste0("simmerge",i,"$Date"))) >= Caldates[1] & eval(parse(text = paste0("simmerge",i,"$Date"))) <= Caldates[2], ])
  assign(paste0("valsubset",i),eval(parse(text = paste0("simmerge",i)))[eval(parse(text = paste0("simmerge",i,"$Date"))) >= Valdates[1] & eval(parse(text = paste0("simmerge",i,"$Date"))) <= Valdates[2], ])}

for(i in 1:n) { assign(paste0("simmergesm",i), merge(obsws32sm,eval(parse(text = paste0("cwws32_run",i,"$bd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("calsubsetsm",i),eval(parse(text = paste0("simmergesm",i)))[eval(parse(text = paste0("simmergesm",i,"$Date"))) >= Caldates[1] & eval(parse(text = paste0("simmergesm",i,"$Date"))) <= Caldates[2], ])
  assign(paste0("valsubsetsm",i),eval(parse(text = paste0("simmergesm",i)))[eval(parse(text = paste0("simmergesm",i,"$Date"))) >= Valdates[1] & eval(parse(text = paste0("simmergesm",i,"$Date"))) <= Valdates[2], ])}

# simmerge1<- merge(obsws32,eval(parse(text = paste0("cwws32_run",i,"$bd"))), by.x = "Date", by.y="date", all = FALSE)
#simmergesm1<- merge(observedsubsetsm,eval(parse(text = paste0("cwws32_run",i,"$bd"))), by.x = "Date", by.y="date", all = FALSE)


#subset observed data to calibration dates
# calsubset <- eval(parse(text = paste0("simmerge",i)))[eval(parse(text = paste0("simmerge",i,"$Date"))) >= Caldates[1] & eval(parse(text = paste0("simmerge",i,"$Date"))) <= Caldates[2], ]

#calsubsetsm <- observedsubsetsm[observedsubsetsm$Date >= Caldates[1] & observedsubsetsm$Date <= Caldates[2], ]
```

Calculate calibration performance metrics

```{r calculate fit values and append them to a list, fig.height=9, fig.width=14, paged.print=TRUE}
setwd(system.file("extdata/", package = "RHESSysIOinR"))

NSElist<- c()
lnNSElist<- c()
KGElist<- c()

smNSElist<- c()
smlnNSElist<- c()
smKGElist<- c()

for(i in 1:n) { assign(paste0("NSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("simmerge",i,"$streamflow")))), obs = as.numeric(eval(parse(text = paste0("simmerge",i,"$observedstreamflow")))) ))
  NSElist[[i]]<- eval(parse(text = paste0("NSEobs",i))) }

for(i in 1:n) {  assign(paste0("lnNSEobs",i), NSE( sim = as.numeric(eval(parse(text = paste0("simmerge",i,"$streamflow")))), obs = as.numeric(eval(parse(text = paste0("simmerge",i,"$observedstreamflow")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
  lnNSElist[[i]]<- eval(parse(text = paste0("lnNSEobs",i))) }

for(i in 1:n) {  assign(paste0("KGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("simmerge",i,"$streamflow")))), obs = as.numeric(eval(parse(text = paste0("simmerge",i,"$observedstreamflow"))))))
  KGElist[[i]]<- eval(parse(text = paste0("KGEobs",i))) }

for(i in 1:n) {  assign(paste0("smNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("simmergesm",i,"$rz_storage","/simmergesm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("simmergesm",i,"$mergedsoilmoisture"))))))
  smNSElist[[i]]<- eval(parse(text = paste0("smNSEobs",i))) }

for(i in 1:n) {  assign(paste0("smlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("simmergesm",i,"$rz_storage","/simmergesm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("simmergesm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
  smlnNSElist[[i]]<- eval(parse(text = paste0("smlnNSEobs",i))) }

for(i in 1:n) {  assign(paste0("smKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("simmergesm",i,"$rz_storage","/simmergesm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("simmergesm",i,"$mergedsoilmoisture"))))))
  smKGElist[[i]]<- eval(parse(text = paste0("smKGEobs",i))) }

## modified for calsubset

calNSElist<- c()
callnNSElist<- c()
calKGElist<- c()

calsmNSElist<- c()
calsmlnNSElist<- c()
calsmKGElist<- c()

for(i in 1:n) { assign(paste0("cNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("calsubset",i,"$streamflow")))), obs = as.numeric(eval(parse(text = paste0("calsubset",i,"$observedstreamflow")))) ))
  calNSElist[[i]]<- eval(parse(text = paste0("cNSEobs",i))) }

for(i in 1:n) {  assign(paste0("clnNSEobs",i), NSE( sim = as.numeric(eval(parse(text = paste0("calsubset",i,"$streamflow")))), obs = as.numeric(eval(parse(text = paste0("calsubset",i,"$observedstreamflow")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
  callnNSElist[[i]]<- eval(parse(text = paste0("clnNSEobs",i))) }

for(i in 1:n) {  assign(paste0("cKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("calsubset",i,"$streamflow")))), obs = as.numeric(eval(parse(text = paste0("calsubset",i,"$observedstreamflow"))))))
  calKGElist[[i]]<- eval(parse(text = paste0("cKGEobs",i))) }

for(i in 1:n) {  assign(paste0("csmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("calsubsetsm",i,"$rz_storage","/calsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("calsubsetsm",i,"$mergedsoilmoisture"))))))
  calsmNSElist[[i]]<- eval(parse(text = paste0("csmNSEobs",i))) }

for(i in 1:n) {  assign(paste0("csmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("calsubsetsm",i,"$rz_storage","/calsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("calsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
  calsmlnNSElist[[i]]<- eval(parse(text = paste0("csmlnNSEobs",i))) }

for(i in 1:n) {  assign(paste0("csmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("calsubsetsm",i,"$rz_storage","/calsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("calsubsetsm",i,"$mergedsoilmoisture"))))))
  calsmKGElist[[i]]<- eval(parse(text = paste0("csmKGEobs",i))) }

## modified for val subset

valNSElist<- c()
vallnNSElist<- c()
valKGElist<- c()

valsmNSElist<- c()
valsmlnNSElist<- c()
valsmKGElist<- c()


for(i in 1:n) { assign(paste0("vNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubset",i,"$streamflow")))), obs = as.numeric(eval(parse(text = paste0("valsubset",i,"$observedstreamflow")))) ))
  valNSElist[[i]]<- eval(parse(text = paste0("vNSEobs",i))) }

for(i in 1:n) {  assign(paste0("vlnNSEobs",i), NSE( sim = as.numeric(eval(parse(text = paste0("valsubset",i,"$streamflow")))), obs = as.numeric(eval(parse(text = paste0("valsubset",i,"$observedstreamflow")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
  vallnNSElist[[i]]<- eval(parse(text = paste0("vlnNSEobs",i))) }

for(i in 1:n) {  assign(paste0("vKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("valsubset",i,"$streamflow")))), obs = as.numeric(eval(parse(text = paste0("valsubset",i,"$observedstreamflow"))))))
  valKGElist[[i]]<- eval(parse(text = paste0("vKGEobs",i))) }

for(i in 1:n) {  assign(paste0("vsmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
  valsmNSElist[[i]]<- eval(parse(text = paste0("vsmNSEobs",i))) }

for(i in 1:n) {  assign(paste0("vsmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
  valsmlnNSElist[[i]]<- eval(parse(text = paste0("vsmlnNSEobs",i))) }

for(i in 1:n) {  assign(paste0("vsmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
  valsmKGElist[[i]]<- eval(parse(text = paste0("vsmKGEobs",i))) }

NSElist[1:5]
KGElist[1:5]
lnNSElist[1:5]

Reduce(max, NSElist)
Reduce(max, lnNSElist)
Reduce(max, KGElist)

Reduce(max, smNSElist)
Reduce(max, smlnNSElist)
Reduce(max, smKGElist)

which(NSElist == Reduce(max, NSElist), arr.ind=TRUE)
which(lnNSElist == Reduce(max, lnNSElist), arr.ind=TRUE)
which(KGElist == Reduce(max, KGElist), arr.ind=TRUE)

which(smNSElist == Reduce(max, smNSElist), arr.ind=TRUE)
which(smlnNSElist == Reduce(max, smlnNSElist), arr.ind=TRUE)
which(smKGElist == Reduce(max, smKGElist), arr.ind=TRUE)

paramtable<- read.table(file = "out/cwparamtable091923.txt")

paramtable[which(NSElist == Reduce(max, NSElist), arr.ind=TRUE),]
paramtable[which(lnNSElist == Reduce(max, lnNSElist), arr.ind=TRUE),]
paramtable[which(KGElist == Reduce(max, KGElist), arr.ind=TRUE),]

paramtable[which(smNSElist == Reduce(max, smNSElist), arr.ind=TRUE),]
paramtable[which(smlnNSElist == Reduce(max, smlnNSElist), arr.ind=TRUE),]
paramtable[which(smKGElist == Reduce(max, smKGElist), arr.ind=TRUE),]

# paramtable[7,]

###plot all data for GLUE

paramtable$run<- seq.int(nrow(paramtable))
paramtable$rowname<- row.names(paramtable)

paramtable$NSE<- NSElist
paramtable$lnNSE<- lnNSElist
paramtable$KGE<- KGElist

paramtable$smNSE<- smNSElist
paramtable$smlnNSE<- smlnNSElist
paramtable$smKGE<- smKGElist

#add in calibration values

paramtable$calNSE<- calNSElist
paramtable$callnNSE<- callnNSElist
paramtable$calKGE<- calKGElist

paramtable$calsmNSE<- calsmNSElist
paramtable$calsmlnNSE<- calsmlnNSElist
paramtable$calsmKGE<- calsmKGElist

#add in validation values
paramtable$valNSE<- valNSElist
paramtable$vallnNSE<- vallnNSElist
paramtable$valKGE<- valKGElist

paramtable$valsmNSE<- valsmNSElist
paramtable$valsmlnNSE<- valsmlnNSElist
paramtable$valsmKGE<- valsmKGElist

paramtable<- as.data.frame(lapply(paramtable,unlist))

write.table(paramtable, file = "out/dsmcalibrationoutput1023.txt")


top100<- paramtable[order(-paramtable$lnNSE),][1:100,]

top100$run

### use values from top 100 run to table of daily streamflow predictions, for each day predict 95% prediction interval and mean then plot
#subset streamflow value for each day - day 1 day 2 etc
#put all values into a table

top100[["run"]]

toppredictions<- data.frame(cwws32_run1$bd$date)

for (i in top100$run){
 # print(i)
  toppredictions[,ncol(toppredictions)+1] <- eval(parse(text=paste0("cwws32_run",i,"$bd$streamflow")))
  colnames(toppredictions)[ncol(toppredictions)] <- paste0("stream",i)
}

head(toppredictions[1:5,])

toppredictions<- toppredictions[,-1]

toppredictions$upper<- 0
toppredictions$mean<- 0
toppredictions$lower<- 0

for (i in 1:nrow(toppredictions)){
 #  print(i)
  upper= CI(as.numeric(toppredictions[i,]),ci=0.95)[1]
  mean= CI(as.numeric(toppredictions[i,]),ci=0.95)[2]
  lower= CI(as.numeric(toppredictions[i,]),ci=0.95)[3]
  
  toppredictions[i,]$upper<- upper
  toppredictions[i,]$mean<- mean
  toppredictions[i,]$lower<- lower
}

toppredictions<-cbind(date = cwws32_run1$bd$date,toppredictions)

head(toppredictions[1:5,])

# toppredictions[1:500,]

ggplot(toppredictions,aes(date,mean,group=1))+
  geom_line(col = 'red')+
  geom_ribbon(aes(ymin=lower, ymax=upper), fill = "blue", alpha=0.3)+
  geom_line(data=calsubset1,aes(x=Date,y=discharge_mm))+
  ylab("Discharge mm")+
  xlab("Date")+
  labs(title = "Top 100 Model Runs vs Measured Streamflow")


par(mfrow=c(1, 1))

{plot(paramtable$m,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - M", main = "M - Decay of hydraulic conductivity with depth")
abline(h=0,lty=2)}
{plot(paramtable$k,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - K", main = "K - Hydraulic conductivity at the surface")
abline(h=0,lty=2)}
{plot(paramtable$soil_dep,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - Sd", main = "Sd - soil depth")
abline(h=0,lty=2)}
{plot(paramtable$m_v,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - Mv", main = "Mv - Vertical decay of hydraulic conductivity with depth")
abline(h=0,lty=2)}
{plot(paramtable$k_v,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - Kv", main = "Kv - Vertical hydraulic conductivity at the surface")
abline(h=0,lty=2)}
{plot(paramtable$gw1,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - GW1", main = "GW1 - Saturated to Groundwater Coefficient")
abline(h=0,lty=2)}
{plot(paramtable$gw2,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - GW2", main = "GW2 - Groundwater Loss Coefficient")
abline(h=0,lty=2)}

{plot(paramtable$pa,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - pa", main = "pa - Pore Size Index Multiplier")
abline(h=0,lty=2)}
{plot(paramtable$po,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - po", main = "po - PSI Air Entry Multiplier")
abline(h=0,lty=2)}
{plot(paramtable$vgseng1,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - vgseng1", main = "vgseng1 - Specific Leaf Area Multiplier")
abline(h=0,lty=2)}
{plot(paramtable$vgseng2,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - vgseng2", main = "vgseng2 - Ratio of Shaded to Sunlit Modifier")
abline(h=0,lty=2)}
{plot(paramtable$vgseng3,paramtable$NSE, pch = 20,ylab="Nash-Sutcliffe model efficiency coefficient", xlab = "Multiplier - vgseng3", main = "vgseng3 - NOT USED")
abline(h=0,lty=2)}


old.par <- par(mfrow=c(3, 7), mar = c(5,4,4,2))

plot(paramtable$m,paramtable$NSE,xlab = "m parameter", pch = 20)
lines(lowess(paramtable$m,paramtable$NSE, f = 0.1),col="red",ylim = c(-1,0.7))
plot(paramtable$k,paramtable$NSE,xlab = "lateral ksat parameter", pch = 20)
lines(lowess(paramtable$k,paramtable$NSE, f = 0.1),col="red",ylim = c(-1,0.7))
plot(paramtable$soil_dep,paramtable$NSE,xlab = "sdepth parameter", pch = 20)
lines(lowess(paramtable$soil_dep,paramtable$NSE, f = 0.1),col="red",ylim = c(-1,0.7))
plot(paramtable$m_v,paramtable$NSE,xlab = "mv parameter", pch = 20)
lines(lowess(paramtable$m_v,paramtable$NSE, f = 0.1),col="red",ylim = c(-1,0.7))
plot(paramtable$k_v,paramtable$NSE,xlab = "ksatv parameter", pch = 20)
lines(lowess(paramtable$k_v,paramtable$NSE, f = 0.1),col="red",ylim = c(-1,0.7))
plot(paramtable$gw1,paramtable$NSE,xlab = "gw1 parameter", pch = 20)
lines(lowess(paramtable$gw1,paramtable$NSE, f = 0.1),col="red",ylim = c(-1,0.7))
plot(paramtable$gw2,paramtable$NSE,xlab = "gw2 parameter", pch = 20)
lines(lowess(paramtable$gw2,paramtable$NSE, f = 0.1),col="red",ylim = c(-1,0.7))


plot(paramtable$m,paramtable$lnNSE,ylim = c(-1,0.7),xlab = "m parameter", pch = 20)
lines(lowess(paramtable$m,paramtable$lnNSE, f = 0.1),col="red")
plot(paramtable$k,paramtable$lnNSE,ylim = c(-1,0.7),xlab = "lateral ksat parameter", pch = 20)
lines(lowess(paramtable$k,paramtable$lnNSE, f = 0.1),col="red")
plot(paramtable$soil_dep,paramtable$lnNSE,ylim = c(-1,0.7),xlab = "sdepth parameter", pch = 20)
lines(lowess(paramtable$soil_dep,paramtable$lnNSE, f = 0.1),col="red")
plot(paramtable$m_v,paramtable$lnNSE,ylim = c(-1,0.7),xlab = "mv parameter", pch = 20)
lines(lowess(paramtable$m_v,paramtable$lnNSE, f = 0.1),col="red")
plot(paramtable$k_v,paramtable$lnNSE,ylim = c(-1,0.7),xlab = "ksatv parameter", pch = 20)
lines(lowess(paramtable$k_v,paramtable$lnNSE, f = 0.1),col="red")
plot(paramtable$gw1,paramtable$lnNSE,ylim = c(-1,0.7),xlab = "gw1 parameter", pch = 20)
lines(lowess(paramtable$gw1,paramtable$lnNSE, f = 0.1),col="red")
plot(paramtable$gw2,paramtable$lnNSE,ylim = c(-1,0.7),xlab = "gw2 parameter", pch = 20)
lines(lowess(paramtable$gw2,paramtable$lnNSE, f = 0.1),col="red")


plot(paramtable$m,paramtable$KGE,ylim = c(-0.25,1),xlab = "m parameter", pch = 20)
lines(lowess(paramtable$m,paramtable$KGE, f = 0.1),col="red")
plot(paramtable$k,paramtable$KGE,ylim = c(-0.25,1),xlab = "lateral ksat parameter", pch = 20)
lines(lowess(paramtable$k,paramtable$KGE, f = 0.1),col="red")
plot(paramtable$soil_dep,paramtable$KGE,ylim = c(-0.25,1),xlab = "sdepth parameter", pch = 20)
lines(lowess(paramtable$soil_dep,paramtable$KGE, f = 0.1),col="red")
plot(paramtable$m_v,paramtable$KGE,ylim = c(-0.25,0.7),xlab = "mv parameter", pch = 20)
lines(lowess(paramtable$m_v,paramtable$KGE, f = 0.1),col="red")
plot(paramtable$k_v,paramtable$KGE,ylim = c(-0.25,0.7),xlab = "ksatv parameter", pch = 20)
lines(lowess(paramtable$k_v,paramtable$KGE, f = 0.1),col="red")
plot(paramtable$gw1,paramtable$KGE,ylim = c(-0.25,0.7),xlab = "gw1 parameter", pch = 20)
lines(lowess(paramtable$gw1,paramtable$KGE, f = 0.1),col="red")
plot(paramtable$gw2,paramtable$KGE,ylim = c(-0.25,0.7),xlab = "gw2 parameter", pch = 20)
lines(lowess(paramtable$gw2,paramtable$KGE, f = 0.1),col="red")

par(old.par)

old.par <- par(mfrow=c(1, 12), mar = c(5,4,4,2))

plot(paramtable$m,paramtable$smKGE,ylim = c(-0.25,1),xlab = "m parameter", pch = 20)
lines(lowess(paramtable$m,paramtable$smKGE, f = 0.1),col="red")
plot(paramtable$k,paramtable$smKGE,ylim = c(-0.25,1),xlab = "lateral ksat parameter", pch = 20)
lines(lowess(paramtable$k,paramtable$smKGE, f = 0.1),col="red")
plot(paramtable$soil_dep,paramtable$smKGE,ylim = c(-0.25,1),xlab = "sdepth parameter", pch = 20)
lines(lowess(paramtable$soil_dep,paramtable$smKGE, f = 0.1),col="red")
plot(paramtable$m_v,paramtable$smKGE,ylim = c(-0.25,0.7),xlab = "mv parameter", pch = 20)
lines(lowess(paramtable$m_v,paramtable$smKGE, f = 0.1),col="red")
plot(paramtable$k_v,paramtable$smKGE,ylim = c(-0.25,0.7),xlab = "ksatv parameter", pch = 20)
lines(lowess(paramtable$k_v,paramtable$smKGE, f = 0.1),col="red")
plot(paramtable$gw1,paramtable$smKGE,ylim = c(-0.25,0.7),xlab = "gw1 parameter", pch = 20)
lines(lowess(paramtable$gw1,paramtable$smKGE, f = 0.1),col="red")
plot(paramtable$gw2,paramtable$smKGE,ylim = c(-0.25,0.7),xlab = "gw2 parameter", pch = 20)
lines(lowess(paramtable$gw2,paramtable$smKGE, f = 0.1),col="red")

plot(paramtable$pa,paramtable$smKGE,ylim = c(-0.25,1),xlab = "pore size index", pch = 20)
lines(lowess(paramtable$pa,paramtable$smKGE, f = 0.1),col="red")
plot(paramtable$po,paramtable$smKGE,ylim = c(-0.25,0.7),xlab = "psi air entry", pch = 20)
lines(lowess(paramtable$po,paramtable$smKGE, f = 0.1),col="red")
plot(paramtable$vgseng1,paramtable$smKGE,ylim = c(-0.25,0.7),xlab = "vgseng1", pch = 20)
lines(lowess(paramtable$vgseng1,paramtable$smKGE, f = 0.1),col="red")
plot(paramtable$vgseng2,paramtable$smKGE,ylim = c(-0.25,0.7),xlab = "vgseng2", pch = 20)
lines(lowess(paramtable$vgseng2,paramtable$smKGE, f = 0.1),col="red")
plot(paramtable$vgseng3,paramtable$smKGE,ylim = c(-0.25,0.7),xlab = "vgseng3", pch = 20)
lines(lowess(paramtable$vgseng3,paramtable$smKGE, f = 0.1),col="red")

par(old.par)

### end plot all data for GLUE

paste0("cwws32_run",which(NSElist == Reduce(max, NSElist), arr.ind=TRUE),"$bd$streamflow")
paste0("cwws32_run",which(lnNSElist == Reduce(max, lnNSElist), arr.ind=TRUE),"$bd$streamflow")
paste0("cwws32_run",which(KGElist == Reduce(max, KGElist), arr.ind=TRUE),"$bd$streamflow")


{plot(cwws32_run33$bd$date,cwws32_run33$bd$streamflow, type = "l", col = 'red', main = "Observed Streamflow vs Top Runs", xlab = "Date", ylab = "Streamflow")
lines(cwws32_run65$bd$date,cwws32_run65$bd$streamflow, col = 'blue')
#lines(cwws32_run46$bd$date,cwws32_run46$bd$streamflow, col = 'green')
lines(simmerge1$Date,simmerge1$observedstreamflow, col = 'orange', lwd = 2, lty = 2)}


#{plot(paste("cwws32_run",which(NSElist == Reduce(max, NSElist), arr.ind=TRUE),"$bd$date", sep = ""),paste("cwws32_run",which(NSElist == Reduce(max, NSElist), arr.ind=TRUE),"$bd$streamflow", sep = ""), type = "l", col = 'red', main = "Observed Streamflow vs Top Runs", xlab = "Date", ylab = "Streamflow")
#lines(paste("cwws32_run",which(lnNSElist == Reduce(max, lnNSElist), arr.ind=TRUE),"$bd$date", sep = ""),paste("cwws32_run",which(lnNSElist == Reduce(max, lnNSElist), arr.ind=TRUE),"$bd$streamflow", sep = ""), col = 'blue')
#lines(cwws32_run80$bd$date,cwws32_run80$bd$streamflow, col = 'green')
#lines(paste("cwws32_run",which(KGElist == Reduce(max, KGElist), arr.ind=TRUE),"$bd$date", sep = ""),paste("cwws32_run",which(KGElist == Reduce(max, KGElist), arr.ind=TRUE),"$bd$streamflow", sep = ""), col = 'orange', lwd = 2, lty = 2)
#legend("topleft",inset = 0.05, legend=c("Oberved Discharge","Best NSE","BEST lnNSE","Best KGE"), col=c("orange","red","blue","green"), lty=c(2,1,1,1))}

{plot(cwws32_run24$bd$date,cwws32_run24$bd$streamflow, type = "l", col = 'red', main = "Observed Streamflow vs Top Runs", xlab = "Date", ylab = "Streamflow", ylim = c(0,10))
#lines(cwws32_run47$bd$date,cwws32_run47$bd$streamflow, col = 'blue')
lines(obsws32$Date,obsws32$discharge_mm, col = 'black', lwd = 2, lty = 2)}

```

*** VALIDATION ***

Run Model once for validation, copied from previous code must clean up


Configure RHESSys Inputs/Outputs for a single run.

Use World Statefile created during spin-up. To run model one time at patch scale.

 COMMAND LINE OPTIONS

-b		Basin output option.  Print out response variables for specified basins. 
-c		Canopy stratum output option.  Print out response variables for specified strata. 
-g		Grow option.  Try to read in dynamic bgc input data and output dynamic bgc parameters. 
-h    Hillslope output option.  Print out response variables for specified hillslopes. 
-p		Patch output option.  Print out response variables for specified patches. 
-r		Routing option. Gives name of flow_table to define explicit routing connectivity.  Also trigger use of explicit routing over TOPMODEL approach. 
-c		Stratum output option.  Print out response variables for specified strata. 


patches listed top to bottom

```{r Configure RHESSys Inputs for Validation}

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32",
  flowtable = "CWWS321.flow",
  start = "2013 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32",
#  commandline_options = c("-b -g -p"))
 
 commandline_options = c("-b -p"))

#commandline_options = c("-b -g -p 1 110 136557 136557 -p 1 108 141942 141942 -p 1 108 149478 149478"))
#1 107 141942 136557
#1 107 149478 136557

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created
input_tec_data = IOin_tec_std(start = "2015 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")

## Calibrated Values 

which(NSElist == Reduce(max, NSElist), arr.ind=TRUE)
which(lnNSElist == Reduce(max, lnNSElist), arr.ind=TRUE)
which(KGElist == Reduce(max, KGElist), arr.ind=TRUE)

which(smNSElist == Reduce(max, smNSElist), arr.ind=TRUE)
which(smlnNSElist == Reduce(max, smlnNSElist), arr.ind=TRUE)
which(smKGElist == Reduce(max, smKGElist), arr.ind=TRUE)

paramtable[which(NSElist == Reduce(max, NSElist), arr.ind=TRUE),]
paramtable[which(lnNSElist == Reduce(max, lnNSElist), arr.ind=TRUE),]
paramtable[which(KGElist == Reduce(max, KGElist), arr.ind=TRUE),]

paramtable[which(smNSElist == Reduce(max, smNSElist), arr.ind=TRUE),]
paramtable[which(smlnNSElist == Reduce(max, smlnNSElist), arr.ind=TRUE),]
paramtable[which(smKGElist == Reduce(max, smKGElist), arr.ind=TRUE),]

stdpars<- IOin_std_pars(
            m = 1.581785,
            k = 41.12945,
            soil_dep= 0.1776117,
            m_v = 8.11574,
            k_v = 0.8713272,
            gw1 = 0.2477113,
            gw2 = 0.4291277,
            pa = 0.3913392,
            po = 1.85424,
            vgseng1 = 1.459184,
            vgseng2 = 1.799894,
            vgseng3 = 1.381696)

#change_def_file()
#test<- IOin_def_pars_simple(as.list("soil_shallowloam.def","porosity_decay", "1000", n = 150 ))

```

Run RHESSys once for validation

```{r Run Rhessys Once for Validation, eval=FALSE, include=FALSE}

start_time = Sys.time()
run_rhessys_single(input_rhessys = input_rhessys,
                   hdr_files = input_hdr,
                   tec_data = input_tec_data,
                   std_pars = stdpars,
                   runID = 'validation')
end_time = Sys.time()
end_time - start_time

```

Read RHESSys Single Run Output

```{r Read in RHESSys Validation Output}

getwd()

singlerunvalidation<- readin_rhessys_output("out/cwws32_runvalidation")

plot(singlerunvalidation$bd$streamflow~singlerunvalidation$bd$date, type = "l", main = "Streamflow", xlab = "Date", ylab = "Streamflow", col = 'DarkBlue')

plot(as.Date(singlerunvalidation$bd$date),singlerunvalidation$bd$rz_storage, type = "l", col = 'black', main = "Basin Scale Root Zone Storage",
    xlab = "Date", ylab = "mm")

#basin scale soil moisture
plot(singlerunvalidation$bd$rz_storage/singlerunvalidation$bdg$root_depth~singlerunvalidation$bd$date, type = "l", main = "RZ_Storage/Root_Depth x Date", xlab = "Date", ylab = "rz_Storage/root_depth", col = 'brown')

plot(singlerunvalidation$bd$lai~singlerunvalidation$bd$date, type = "l", main = "LAI", xlab = "Date", ylab = "LAI", col = 'DarkGreen')
plot(singlerunvalidation$bd$pet~singlerunvalidation$bd$date, type = "l", main = "Potential Evapotranspiration", xlab = "Date", ylab = "PET", col = 'DarkBlue')
plot(singlerunvalidation$bd$et~singlerunvalidation$bd$date, type = "l", main = "Evapotranspiration", xlab = "Date", ylab = "ET", col = 'darkslategray')

plot((singlerunvalidation$bd$unsat_stor/singlerunvalidation$bd$sat_def_z)~singlerunvalidation$bd$date, type = "l", main = "unsat_stor/sat_def_z", xlab = "Date", ylab = "vwc", col = 'DarkGreen')


```

Merge Observed and Simulated Data

```{r Merge Observed and Simulated Validation Datasets}
## merge values instead of subsetting to match up with simulated dates
singlerunvalidation$bd<- merge(singlerunvalidation$bd,obsws32, by.x = "date", by.y = "Date", all = FALSE)

## merge soil moisture values but include all data
singlerunvalidation$data <-merge(singlerunvalidation$bd,obsws32sm, by.x = "date", by.y = "Date", all = TRUE)
```

Plot Observed and Simulated Data, Plot RHESSys Outputs

```{r Plot Observed and Simulated Validation Datasets}
## Plot Hydrograph comparing modeled and observed streamflow
{hydrograph(input=singlerunvalidation$bd, streamflow=singlerunvalidation$bd$observedstreamflow, streamflow2 = singlerunvalidation$bd$streamflow, timeSeries = singlerunvalidation$bd$date, precip = singlerunvalidation$bd$streamflow,
           P.units = "mm", S.units = "mm normalized by basin area", S1.col = 'Blue', S2.col = 'Red')

legend("topleft",inset = .2, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("blue","red"), lty=1:2)}

{plot(singlerunvalidation$data$date,singlerunvalidation$data$observedstreamflow.x, type = "l", xlab = "Date", ylab = "Streamflow", main = "Predicted vs Observed Streamflow")
lines(singlerunvalidation$data$date, singlerunvalidation$data$streamflow, col = 'RED')
legend("topright",inset = 0, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("black","red"), lty=1:1)}

{plot(singlerunvalidation$data$date,singlerunvalidation$data$observedstreamflow.x, type = "l", xlab = "Date", ylab = "Streamflow", main = "Predicted vs Observed Log Streamflow", log = "y")
lines(singlerunvalidation$data$date, singlerunvalidation$data$streamflow, col = 'RED')
legend("topright",inset = 0, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("black","red"), lty=1:1)}

predictedvsobservedstreamlm<- lm(observedstreamflow~streamflow, data = singlerunvalidation$bd)

{plot(singlerunvalidation$bd$observedstreamflow,singlerunvalidation$bd$streamflow, xlab = "Observed", ylab = "Predicted", main = "Predicted vs Observed Streamflow", xlim = c(0,55), ylim = c(0,55))
abline(a=0, b=1, col = 'RED', lty = 2, lwd = 2)
legend("right",inset = 0.01, legend = paste("R2 =",format(summary(predictedvsobservedstreamlm)$r.squared,digits=3)))}

{plot(singlerunvalidation$data$date,(singlerunvalidation$data$rz_storage/singlerunvalidation$data$rootdepth), type = "l", ylim = c(0,0.35), xlab = "Date", ylab = "RZ_Storage/Rootdepth", main = "Predicted vs Observed Basin Scale Soil Moisture")
lines(singlerunvalidation$data$date, singlerunvalidation$data$mergedsoilmoisture, col = 'RED')
legend("topright",inset = 0, legend=c("Observed Soil Moisture","Predicted Soil Moisture"), col=c("black","red"), lty=1:1)}

predictedvsobservedsoillm<- lm((rz_storage/rootdepth)~mergedsoilmoisture, data = singlerunvalidation$data)

{plot((singlerunvalidation$data$rz_storage/singlerunvalidation$data$rootdepth),singlerunvalidation$data$mergedsoilmoisture, xlab = "Observed", ylab = "Predicted", main = "Predicted vs Observed Basin Scale Soil Moisture", xlim = c(0.05,0.4), ylim = c(0.05,0.4))
abline(a=0, b=1, col = 'RED', lty = 2, lwd = 2)
legend("right",inset = 0.01, legend = paste("R2 =",format(summary(predictedvsobservedsoillm)$r.squared,digits=3)))}

## Plot other model outputs

par(mfrow=c(5,1), mar = c(2,5,4,2))

plot(singlerunvalidation$bd$date,singlerunvalidation$bd$tmin, type = "l", col = 'BLUE', ylim = c(-15,30), ylab = "Temperature", xlab = "Date")
lines(singlerunvalidation$bd$date,singlerunvalidation$bd$tmax, type = "l", col = 'RED')
plot(singlerunvalidation$bd$date,singlerunvalidation$bd$precip, type = "h", ylab = "Precipitation", xlab = "Date")
plot(singlerunvalidation$bd$date,singlerunvalidation$bd$streamflow, type = "l", ylab = "Streamflow", xlab = "Date", col = 'blue')
plot(singlerunvalidation$bd$date,singlerunvalidation$bd$baseflow, type = "l", ylab = "Baseflow", xlab = "Date", col = 'brown')
plot(singlerunvalidation$bd$date,singlerunvalidation$bd$rz_storage, type = "l", ylab = "RZ Storage", xlab = "Date", col = 'dark green')
plot(singlerunvalidation$bd$date,singlerunvalidation$bd$psn ,type = "l", ylab = "PSN", xlab = "Date")
plot(singlerunvalidation$bd$date,singlerunvalidation$bd$et, type = "l", ylab = "Evaoptranspiration", xlab = "Date")
plot(singlerunvalidation$bd$date,singlerunvalidation$bd$pet, type = "l", ylab = "PET", xlab = "Date")
plot(singlerunvalidation$bd$date,singlerunvalidation$bd$gw.Qout, type = "l", ylab = "Q out", xlab = "Date")
plot(singlerunvalidation$bd$date,singlerunvalidation$bd$gw.storage, type = "l", ylab = "GW Storage", xlab = "Date")

par(mfrow=c(1,1))

### will only plot in growth mode , used to check that vegetation is initialized properly ##
plot(singlerunvalidation$bdg$date, singlerunvalidation$bdg$lai, type = "l", main = "LAI", xlab = "Date", col = 'dark green')
plot(singlerunvalidation$bdg$date, singlerunvalidation$bdg$soilc, type = "l", main = "Soil Carbon", xlab = "Date", col = 'brown')


## plot cal/val sets

{plot(singlerunvalidation$data$date,(singlerunvalidation$data$rz_storage/singlerunvalidation$data$rootdepth), type = "l", ylim = c(0,0.35), xlab = "Date", ylab = "RZ_Storage/Rootdepth", main = "Predicted vs Observed Basin Scale Soil Moisture")
lines(obsws32smcal$Date,obsws32smcal$mergedsoilmoisture, col = "BLUE")
lines(obsws32smval$Date,obsws32smval$mergedsoilmoisture, col = "RED")
legend("topright",inset = 0, legend=c("Predicted Soil Moisture","Observed Calibration Soil Moisture", "Observed Validation Soil Moisture"), col=c("black","blue","red"), lty=c(1,1,1))}

{plot(singlerunvalidation$data$date,singlerunvalidation$data$streamflow, type = "l", xlab = "Date", ylab = "Streamflow", main = "Predicted vs Observed Basin Scale Streamflow")
lines(obsws32cal$Date,obsws32cal$observedstreamflow, col = "BLUE")
lines(obsws32val$Date,obsws32val$observedstreamflow, col = "RED")
legend("topright",inset = 0, legend=c("Predicted Streamflow","Observed Calibration Streamflow", "Observed Validation Streamflow"), col=c("black","blue","red"), lty=c(1,1,1))}
```

Spatial Data import and display of inputs

```{r Display Spatial Inputs and Simulated Validation Soil Moisture, fig.height=10, fig.width=14}
# Original input maps have been cropped before processing in R, without cropping the RHESSYs preparation in the R environment will not function properly, below are the input maps used by R
ws32<- raster("grassexport/cwt_ws32/basin_ws32.tif")
patches<- raster("grassexport/cwt_ws32/patch.tif")
acc10<- raster("grassexport/cwt_ws32/acc10.tif")
aspect10<- raster("grassexport/cwt_ws32/aspect10.tif")
#bt1000<- raster("C:/Users/Carlos/Documents/R/win-library/4.0/RHESSysIOinR/extdata/rasters/cwt_ws32/ws32/b.t1000.tif")
dem10<- raster("grassexport/cwt_ws32/dem10.tif")
dem10f<- raster("grassexport/cwt_ws32/dem10f.tif")
dir10<- raster("grassexport/cwt_ws32/dir10.tif")
drain10<- raster("grassexport/cwt_ws32/drain10.tif")
#ht1000<- raster("C:/Users/Carlos/Documents/R/win-library/4.0/RHESSysIOinR/extdata/rasters/cwt_ws32/ws32/h.t1000.tif")
hillslope<- raster("grassexport/cwt_ws32/hillslope.tif")
roads<- brick("grassexport/cwt_ws32/roads.tif")
#shade10<- raster("C:/Users/Carlos/Documents/R/win-library/4.0/RHESSysIOinR/extdata/rasters/cwt_ws32/ws32/shade10.tif")
slope10<- raster("grassexport/cwt_ws32/slope10.tif")
streams<- raster("grassexport/cwt_ws32/streams.tif")
topidx10<- raster("grassexport/cwt_ws32/topidx10_100.tif")
#xmap<- raster("C:/Users/Carlos/Documents/R/win-library/4.0/RHESSysIOinR/extdata/rasters/cwt_ws32/ws32/xmap.tif")
#ymap<- raster("C:/Users/Carlos/Documents/R/win-library/4.0/RHESSysIOinR/extdata/rasters/cwt_ws32/ws32/ymap.tif")


plot(ws32, main ="ws32")
plot(patches, main = "patches")
plot(acc10, main = "acc10")
plot(aspect10, main = "aspect10")
#levelplot(bt1000, col.regions = brewer.pal(name='Spectral', n = 11),at=seq(0,6500,1))
#plot(bt1000, main = "bt1000")
plot(dem10, main = "dem10")
plot(dem10f, main = "dem10f")
plot(dir10, main = "dir10")
plot(drain10, main = "drain10")
#plot(ht1000, main = "ht1000")
{plot(hillslope, main = "hillslope")
  points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", lwd = 1)}
plot(roads, main = "roads")
#plot(shade10, main = "shade10")
plot(slope10, main = "slope10")
plot(streams, main = "streams")
plot(topidx10, main = "topidx10")
#plot(xmap, main = "xmap")
#plot(ymap, main = "ymap")

```

Show locations of measured soil moisture and soil maps

```{r Display Locations of Observed Soil Moisture, fig.height=10, fig.width=10}

colorramp<- viridis(128)

{plot(dem10, col = colorramp, main = "Coweeta Observed Soil Moisture Locations")
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", lwd = 1)}


matrix(c(ObservedSMLocations$Name[3],ObservedSMLocations$Name[4],ObservedSMLocations$Name[5],ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1],ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), nrow = 3, ncol = 3)


{plot(soilstaticmap, col = colorramp, main = "Coweeta Observed Soil Moisture Locations on Static Soil Map")
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", lwd = 1)}

{plot(soilssurgo, col = colorramp, main = "Coweeta Observed Soil Moisture Locations on SSURGO Soil Map")
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", lwd = 1)}

{plot(soildsm, col = colorramp, main = "Coweeta Observed Soil Moisture Locations on RSS Soil Map")
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", lwd = 1)}





```

Display outputs from model run

```{r Display Spatial Outputs and Simulated Validation Soil Moisture, fig.height=10, fig.width=14}
## Extract values for single date
displayday <- singlerunvalidation$pd[which(singlerunvalidation$pd$date=="2018-03-21")]

## reclassify all patches to na and then reclassify to model output values
reclass_all<- c(-2147483648, 2147483647,NA)
reclass_allm<- matrix(reclass_all, ncol = 3, byrow = TRUE)
displaydaypatches<- reclassify(patches,reclass_allm)

displayday$calculatedrzsm <- displayday$rz_storage/displayday$root.depth

reclass_displayday <- cbind(displayday$patchID,displayday$calculatedrzsm)
reclass_displayday <- as.matrix(reclass_displayday)

displaydaypatches<- reclassify(patches,reclass_displayday)

## Plot Spatial Data Output for RZ Storage
#plot(displaydaypatches, xlim = c(280900,282500), ylim = c(4870000,4872000))

{plot(mask(displaydaypatches,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600))
title("CW WS32 RZ Soil Moisture Prediction for 1 day", line = -2)
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", cex = 2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}


reclass_displayday <- cbind(displayday$patchID,displayday$root.depth)
reclass_displayday <- as.matrix(reclass_displayday)
displaydaypatches2<- reclassify(patches,reclass_displayday)

{plot(mask(displaydaypatches2,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600))
title("CW WS32 root.depth Prediction for 1 day", line = -2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}


reclass_displayday <- cbind(displayday$patchID,displayday$rz_storage)
reclass_displayday <- as.matrix(reclass_displayday)
displaydaypatches3<- reclassify(patches,reclass_displayday)

{plot(mask(displaydaypatches3,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600))
title("CW WS32 rz_storage Prediction for 1 day", line = -2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}

reclass_displayday <- cbind(displayday$patchID,displayday$sat_def)
reclass_displayday <- as.matrix(reclass_displayday)
displaydaypatches4<- reclassify(patches,reclass_displayday)

{plot(mask(displaydaypatches4,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600))
title("CW WS32 Saturation Deficit Prediction for 1 day in mm", line = -2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}

reclass_displayday <- cbind(displayday$patchID,(displayday$unsat_stor/displayday$sat_def_z))
reclass_displayday <- as.matrix(reclass_displayday)
displaydaypatches5<- reclassify(patches,reclass_displayday)

{plot(mask(displaydaypatches5,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600))
title("CW WS32 unsaturated soil moisture vwc Prediction for 1 day", line = -2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}


reclass_displayday <- cbind(displayday$patchID,((displayday$root_zone.S*displayday$potential_rz_store)/displayday$root.depth))
reclass_displayday <- as.matrix(reclass_displayday)
displaydaypatches6<- reclassify(patches,reclass_displayday)

{plot(mask(displaydaypatches6,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600), zlim = c(0,0.50))
title("CW WS32 Rooting Depth VWC Prediction for 1 day", line = -2)
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", cex = 2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}

{plot(mask(displaydaypatches,ws32), xlim = c(275000,276200), ylim = c(3881000,3881600), zlim = c(0,0.50))
title("CW WS32 RZ Soil Moisture Prediction for 1 day", line = -2)
points(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1]), c(ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), pch = 21, col = "black", bg = "red", cex = 2)
scalebar(200, xy=c(275200, 3880800), type='line',divs = "2")}




## Plot Hydrograph
{hydrograph(input=singlerunvalidation$bd, streamflow=singlerunvalidation$bd$observedstreamflow, streamflow2 = singlerunvalidation$bd$streamflow, timeSeries = singlerunvalidation$bd$date, precip = singlerunvalidation$bd$streamflow,
           P.units = "mm", S.units = "mm normalized by basin area", S1.col = 'Blue', S2.col = 'Red')
legend("topleft",inset = .2, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("blue","red"), lty=1:2)}

### end show patch map




patchnumbers<- raster::extract(patches,matrix(c(ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1],ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2]), nrow = 3, ncol = 2))


ObserveSoilMoisturePatches <- matrix(c(ObservedSMLocations$Name[3],ObservedSMLocations$Name[4],ObservedSMLocations$Name[5],ObservedSMLocations[[3]][[3]][1],ObservedSMLocations[[3]][[4]][1],ObservedSMLocations[[3]][[5]][1],ObservedSMLocations[[3]][[3]][2],ObservedSMLocations[[3]][[4]][2],ObservedSMLocations[[3]][[5]][2],patchnumbers), nrow = 3, ncol = 4)


## Extract values for a single patch, select patch ID
ObserveSoilMoisturePatches[1,4]
displaypatch<- singlerunvalidation$pd[which(singlerunvalidation$pd$patchID==ObserveSoilMoisturePatches[1,4])]
ObserveSoilMoisturePatches[2,4]
displaypatch2<- singlerunvalidation$pd[which(singlerunvalidation$pd$patchID==ObserveSoilMoisturePatches[2,4])]
ObserveSoilMoisturePatches[3,4]
displaypatch3<- singlerunvalidation$pd[which(singlerunvalidation$pd$patchID==ObserveSoilMoisturePatches[3,4])]

plot(displaypatch$date,(displaypatch$rz_storage/displaypatch$root.depth), type = "l", xlab = "Date", ylab = "RZ Storage", main = 'CW WS27 More Detailed RZ Storage Patch #147322', ylim = c(0,.4))

{plot(smws32_1mean$Group.1,smws32_1mean$smois30A, type = "l", ylim = c(0,.4), col = 'darkorange', xlim=as.Date(c("2016-10-1","2019-10-1")), main = "CW WS32 More Detailed Soil Moisture vs Patches",
     xlab = "Date", ylab = "Soil Moisture mm")
lines(smws32_2mean$Group.1,smws32_2mean$smois30A,type = "l", col = 'darkred')
lines(smws32_3mean$Group.1,smws32_3mean$smois30A,type = "l", col = 'blue')
lines(displaypatch$date,(displaypatch$rz_storage/displaypatch$root.depth), type = "l", xlab = "Date", ylab = "RZ Storage", col = 'red', lty = 2)
lines(displaypatch2$date,(displaypatch2$rz_storage/displaypatch2$root.depth), type = "l", xlab = "Date", ylab = "RZ Storage", col = 'green', lty = 2)
lines(displaypatch3$date,(displaypatch3$rz_storage/displaypatch3$root.depth), type = "l", xlab = "Date", ylab = "RZ Storage", col = 'black', lty = 2)



# plot(smws32_1mean$smois30A,(displaypatch$rz_storage/displaypatch$root.depth))

legend("bottomleft",inset = .01, legend=c("Observed Patch 1","Predicted Patch 1","Observed Patch 2","Predicted Patch 2","Observed Patch 3","Predicted Patch 3"), col=c("darkorange", "red","darkred","green","blue","black"), lty=c(1,2,1,2,1,2))}

{plot(smws32_2mean$Group.1,smws32_2mean$smois30A, type = "l", ylim = c(0,0.4), col = 'BLUE', xlim=as.Date(c("2016-10-1","2019-10-1")), main = "CW WS32 More Detailed Soil Moisture vs Patch #154914",
     xlab = "Date", ylab = "Soil Moisture mm")
lines(displaypatch$date,(displaypatch$rz_storage/displaypatch$root.depth), type = "l",lwd = 2, xlab = "Date", ylab = "RZ Storage", main = 'CW WS27 More Detailed RZ Storage Patch #154914', col = 'red')
lines(displaypatch$date, ((displaypatch$root_zone.S*displaypatch$potential_rz_store)/displaypatch$root.depth), type = "l", col = "green")
legend("bottomleft",inset = .01, legend=c("Observed Soil Moisture","Predicted Soil Moisture"), col=c("blue","red"), lty=1:1)}


#
#obsws32cal <- obsws32[obsws32$Date >= Caldates[1] & obsws32$Date <= Caldates[2], ]
#obsws32val <- obsws32[obsws32$Date >= Valdates[1] & obsws32$Date <= Valdates[2], ]
#obsws32smcal <- obsws32sm[obsws32sm$Date >= Caldates[1] & obsws32sm$Date <= Caldates[2], ]
#obsws32smval <- obsws32sm[obsws32sm$Date >= Valdates[1] & obsws32sm$Date <= Valdates[2], ]

head(obsws32cal)
head(obsws32val)
head(obsws32smcal)
head(obsws32smval)

#subset Validation range based on Val Dates set by available SM data

validationsubset <- singlerunvalidation$bd[singlerunvalidation$bd$date >= Valdates[1] & singlerunvalidation$bd$date <= Valdates[2], ]

## Fit tests for streamflow

NSE(validationsubset$streamflow,validationsubset$observedstreamflow)

NSE(validationsubset$streamflow,validationsubset$observedstreamflow, FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE)

KGE(validationsubset$streamflow,validationsubset$observedstreamflow)

# Plot Observed and Predicted Streamflow

{plot(validationsubset$date,validationsubset$streamflow, type = 'l', lty = 2, col = 'RED', main = "Validation Subset Observed and Predicted Streamflow")
lines(validationsubset$date,validationsubset$observedstreamflow, type = 'l', col = 'BLACK')
legend("topright",inset = .1, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("black","red"), lty=1:2)}


{plot(singlerunvalidation$bd$date,singlerunvalidation$bd$streamflow, type = 'l', lty = 2, col = 'RED', main = "Observed and Predicted Streamflow")
lines(singlerunvalidation$bd$date,singlerunvalidation$bd$observedstreamflow, type = 'l', col = 'BLACK')
legend("topright",inset = .1, legend=c("Observed Streamflow","Predicted Streamflow"), col=c("black","red"), lty=1:2)}

#Plot Model RZ SM outputs for patch
{plot(displaypatch$date,(displaypatch$rz_storage/displaypatch$root.depth), type = "l",ylim = c(0,0.50), ylab = "Root Zone Storage (mm/m) ", xlab = "Date", main = 'Root Zone Display Patch')
lines(displaypatch$date,(displaypatch$rz_field_capacity/displaypatch$root.depth), type = "l", col = "blue")
lines(displaypatch$date,(displaypatch$rz_wilting_point/displaypatch$root.depth), type = "l", col = "red")
legend("bottomleft",inset = .1, legend=c("Predicted RZ Storage","RZ Field Capacity","RZ Wilting Point"), col=c("black","blue","red"), lty=1:1)}


{plot(displaypatch$date,(displaypatch$unsat_stor/displaypatch$sat_def_z), type = "l",ylim = c(0,0.50), ylab = "Root Zone Storage (mm/m) ", xlab = "Date", main = 'Root Zone Display Patch')
legend("bottomleft",inset = .1, legend=c("Predicted RZ Storage","RZ Field Capacity","RZ Wilting Point"), col=c("black","blue","red"), lty=1:1)}


{plot(smws32_2mean$Group.1,smws32_2mean$smois30A, type = "l", ylim = c(0,0.4), col = 'BLUE', xlim=as.Date(c("2016-10-1","2019-10-1")), main = "CW WS32 More Saturated Zone VWC vs Patch #154914",
     xlab = "Date", ylab = "Soil Moisture mm")
lines(displaypatch$date,(displaypatch$unsat_stor/displaypatch$sat_def_z), type = "l", xlab = "Date", ylab = "RZ Storage", main = 'CW WS27 More Detailed RZ Storage Patch #154914', col = 'red')
legend("bottomleft",inset = .01, legend=c("Observed Soil Moisture","Predicted Soil Moisture"), col=c("blue","red"), lty=1:1)}

```

Model Validation

```{r}

Valdates
## for now run top run and record values

paramtable[which(KGElist == Reduce(max, KGElist), arr.ind=TRUE),]

paramtable[which(smKGElist == Reduce(max, smKGElist), arr.ind=TRUE),]


{plot(cwws32_run136$bd$date,cwws32_run136$bd$streamflow, type = "l", col = 'red', main = "Observed Streamflow vs Top KGE Run", xlab = "Date", ylab = "Streamflow")
lines(obsws32$Date,obsws32$discharge_mm, col = 'orange', lwd = 2, lty = 2)}


valsubset <- simmerge136[simmerge136$Date >= Valdates[1] & simmerge136$Date <= Valdates[2], ]

ValKGE<- KGE(sim = valsubset$streamflow, obs = valsubset$observedstreamflow)


valsubsetsm<- simmergesm136[simmergesm136$Date >= Valdates[1] & simmergesm136$Date <= Valdates[2],]

ValsmKGE<- KGE(sim = valsubsetsm$rz_storage/valsubsetsm$rootdepth, obs = valsubsetsm$mergedsoilmoisture)



ValKGE

ValsmKGE
```

Combine calibration outputs

```{r}
getwd()

dsmdist<- read.csv("out/dsmcalibrationoutput1023.txt", sep=" ")
ssurgodist<- read.csv("out/ssurgocalibrationoutput1023.txt", sep = " ")
staticdist<- read.csv("out/staticcalibrationoutput1023.txt", sep = " ")

paged_table(ssurgodist)
paged_table(dsmdist)
paged_table(staticdist)

ssurgodist$treatment<- 'SSURGO'
dsmdist$treatment<- 'RSS'
staticdist$treatment<- 'Static'


combineddist<- rbind(ssurgodist, dsmdist, staticdist)

ggplot(combineddist, aes(calsmKGE, fill = treatment))+ geom_density(alpha=0.3)

ggplot(combineddist, aes(calKGE, fill = treatment))+ geom_density(alpha=0.3)



smKGEplot<- ggplot(combineddist, aes(calsmKGE, y = treatment, fill = treatment))+ geom_boxplot()+ xlab("Soil Moisture KGE - Calibration") +ylab("Soil Map Input")

KGEplot<- ggplot(combineddist, aes(calKGE, y = treatment, fill = treatment))+ geom_boxplot()+ xlab("Streamflow KGE - Calibration")+ylab(NULL)

ggarrange(smKGEplot,KGEplot, common.legend = TRUE, legend = "top")



smKGEplot<- ggplot(combineddist, aes(calsmKGE, y = treatment, fill = treatment))+ geom_boxplot()+ xlab("Soil Moisture KGE - Calibration") +ylab("Soil Map Input")

KGEplot<- ggplot(combineddist, aes(calKGE, y = treatment, fill = treatment))+ geom_boxplot()+ xlab("Streamflow KGE - Calibration")+ylab(NULL)

ggarrange(smKGEplot,KGEplot, common.legend = TRUE, legend = "top")


text <- "Coweeta Watershed 32 Calibration Performance"
# Create a text grob
tgrob <- text_grob(text,size = 16)
# Draw the text
plot_0 <- as_ggplot(tgrob) + theme(plot.margin = margin(0,3,0,12, "cm"))

ggarrange(plot_0,NULL,smKGEplot,KGEplot,
          ncol = 2,nrow = 2,heights = c(1,5), common.legend = TRUE, legend = "none")




smKGEviolinplot<- ggplot(combineddist, aes(calsmKGE, y = treatment, fill = treatment))+ geom_violin()+ xlab("Soil Moisture KGE - Calibration") +ylab("Soil Map Input")

KGEviolinplot<- ggplot(combineddist, aes(calKGE, y = treatment, fill = treatment))+ geom_violin()+ xlab("Streamflow KGE - Calibration")+ylab(NULL)

ggarrange(smKGEviolinplot,KGEviolinplot, common.legend = TRUE, legend = "top")

library(multcompView)
library(datasets)

oneway.test(valsmKGE~treatment, data= combineddist, var.equal = TRUE)

anova<- aov(valsmKGE~treatment, data = combineddist)

summary(anova)

tukey <- TukeyHSD(anova)
print(tukey)

cld <- multcompLetters4(anova,tukey)

print(cld)



```

Run top n model runs for validation

50/50 weighting

validation will only run 2 years before prediction time period

```{r}
combineddist

plot(ssurgodist$calKGE, ssurgodist$calsmKGE, pch = 19, xlab = "Streamflow KGE", ylab = "Soil Moisture KGE")


combineddist$weightedcal<- rowMeans(combineddist[,c("calKGE","calsmKGE")],)


ordereddist <- combineddist[order(-combineddist$weightedcal),]

ordereddist[ordereddist$treatment=="Static",]


topstatic<- ordereddist[ordereddist$treatment=="Static",]
topssurgo<- ordereddist[ordereddist$treatment=="SSURGO",]
toprss<- ordereddist[ordereddist$treatment=="RSS",]

toprss

```

RSS - prepare to run model n times for patch 1 - only for validation time series

```{r}
 setwd(system.file("extdata/", package = "RHESSysIOinR"))

getwd()

validationruns <- 200

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32dsm.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32dsm",
  flowtable = "CWWS32dsm1.flow",
  start = "2015 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32valrss1",
commandline_options = c("-b -p 1 110 136557 136557"))



#commandline_options = c("-b -g -p 1 110 136557 136557 -p 1 108 141942 141942 -p 1 108 149478 149478"))

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created
input_tec_data = IOin_tec_std(start = "2017 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")


```

RSS - Run RHESSYs

```{r Run RHESSYS in Parallel using foreach RSS 1, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:validationruns, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = toprss[i,]$m,
                            k = toprss[i,]$k,
                            soil_dep= toprss[i,]$soil_dep,
                            m_v = toprss[i,]$m_v,
                            k_v = toprss[i,]$k_v,
                            gw1 = toprss[i,]$gw1,
                            gw2 = toprss[i,]$gw2,
                            pa = toprss[i,]$pa,
                            po = toprss[i,]$po,
                            vgseng1 = toprss[i,]$vgseng1,
                            vgseng2 = toprss[i,]$vgseng2,
                            vgseng3 = toprss[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

RSS - prepare site specific soil moisture datasets, make sure that each patch looks at this
Site 2 at 60cm A was removed from the averaging because of no data

```{r}
#Prepare observed Soil moisture data
obsws32smvalclean<- data.frame(obsws32smval$Date,obsws32smval$mergedsoilmoisture)
names(obsws32smvalclean)<- c('Date','mergedsoilmoisture')

obsws32smvalclean



obsws32smvalclean$Site3<- rowMeans(subset(obsws32smval, select = c(smois30site3a,smois60site3a,smois30site3b,smois60site3b), na.rm = TRUE))
obsws32smvalclean$Site2<- rowMeans(subset(obsws32smval, select = c(smois30site2a,smois30site2b,smois60site2b), na.rm = TRUE))
obsws32smvalclean$Site1<- rowMeans(subset(obsws32smval, select = c(smois30site1a,smois60site1a,smois30site1b,smois60site1b), na.rm = TRUE))



obsws32smvalclean

plot(obsws32smvalclean$Date,obsws32smvalclean$Site3, type = "l", main = "SITE 3 Averaged Sensor Output")

obsws32smvalclean$Site3


{plot(obsws32smvalclean$Date,obsws32smvalclean$mergedsoilmoisture, type = "l", main = "All site averaged sensor output", lty = 3, lwd = 2, ylim = c(0.10,0.35))
lines(obsws32smvalclean$Date,obsws32smvalclean$Site1, col = 'BLUE')
lines(obsws32smvalclean$Date,obsws32smvalclean$Site2, col = 'RED')
lines(obsws32smvalclean$Date,obsws32smvalclean$Site3, col = 'GREEN')}


```

RSS - read 20 runs, create table and append to table for site 1

```{r}
# Read in RHESSys Validation runs
for(i in 1:validationruns) { assign(paste0("cwws32valrss1_run",i), readin_rhessys_output(paste0("out/cwws32valrss1_run",i)))}


plot(cwws32valrss1_run1$pd$date,cwws32valrss1_run1$pd$rz_storage/cwws32valrss1_run1$pd$root.depth, type = "l")





##merge calibration runs with observed so dates match up, instead of subsetting 

for(i in 1:validationruns) { assign(paste0("valmergesm",i), merge(obsws32smvalclean,eval(parse(text = paste0("cwws32valrss1_run",i,"$pd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("valsubsetsm",i),eval(parse(text = paste0("valmergesm",i)))[eval(parse(text = paste0("valmergesm",i,"$date"))) >= Valdates[1] & eval(parse(text = paste0("valmergesm",i,"$date"))) <= Valdates[2], ])}


valmergesm1


validationsmNSElistsite1<- c()
validationsmlnNSElistsite1<- c()
validationsmKGElistsite1<- c()


#for(i in 1:n) {  assign(paste0("vsmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
#  valsmNSElist[[i]]<- eval(parse(text = paste0("vsmNSEobs",i))) }

#for(i in 1:n) {  assign(paste0("vsmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
#  valsmlnNSElist[[i]]<- eval(parse(text = paste0("vsmlnNSEobs",i))) }

for(i in 1:validationruns) {  assign(paste0("vsmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")))), obs = as.numeric(eval(parse(text = paste0("valmergesm",i,"$Site1"))))))
  validationsmKGElistsite1[[i]]<- eval(parse(text = paste0("vsmKGEobs",i))) }


validationsmKGElistsite1


paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")

paste0("valmergesm",i,"$rz_storage","/valmergesm",i,"$root.depth")


```

RSS - Explore Site 1

```{r}

'Exploring Site 1 RSS'


cwws32valrss1_run1

{plot(cwws32valrss1_run1$bd$date, (cwws32valrss1_run1$bd$rz_storage/cwws32valrss1_run1$bd$rootdepth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm1$Date,valmergesm1$Site1, col = 'BLUE', lty = 3)}



{plot(cwws32valrss1_run3$bd$date, (cwws32valrss1_run3$bd$rz_storage/cwws32valrss1_run3$bd$rootdepth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm3$Date,valmergesm3$Site1, col = 'BLUE', lty = 3)}

paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")

plot((valmergesm3$root_zone.S*valmergesm3$potential_rz_store)/(valmergesm3$root.depth), type = "l")
plot(valmergesm3$Date, (valmergesm3$rz_storage/valmergesm3$root.depth), type = "l")
plot(valmergesm3$Date, valmergesm3$Site1, type = "l")


{plot(cwws32valrss1_run3$pd$date, (cwws32valrss1_run3$pd$rz_storage/cwws32valrss1_run3$pd$root.depth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm3$Date,valmergesm3$Site1, col = 'BLUE', lty = 3)}


{plot(cwws32valrss1_run3$pd$date, ((cwws32valrss1_run3$pd$root_zone.S*cwws32valrss1_run3$pd$potential_rz_store)/cwws32valrss1_run3$pd$root.depth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm3$Date,valmergesm3$Site1, col = 'BLUE', lty = 3)}

paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")


{plot(cwws32valrss1_run3$bd$date, (cwws32valrss1_run3$bd$rz_storage/cwws32valrss1_run3$bd$rootdepth), type = 'l', ylim = c(0.0,0.26))
lines(valmergesm3$Date,valmergesm3$Site1, col = 'BLUE', lty = 3)}

{plot(cwws32valrss1_run43$pd$date, (cwws32valrss1_run43$pd$rz_storage/cwws32valrss1_run43$pd$root.depth), type = 'l', ylim = c(0.0,0.26))
lines(valmergesm43$Date,valmergesm43$Site1, col = 'BLUE', lty = 3)}

{plot(cwws32valrss1_run43$bd$date, (cwws32valrss1_run43$bd$rz_storage/cwws32valrss1_run43$bd$rootdepth), type = 'l', ylim = c(0.0,0.26))
lines(valmergesm1$Date,valmergesm1$Site1, col = 'BLUE', lty = 3)}

```

RSS - prepare to run model n times for patch 2 - only for validation time series

```{r}

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32dsm.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32dsm",
  flowtable = "CWWS32dsm1.flow",
  start = "2015 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32valrss2",
 commandline_options = c("-b -p 1 108 141942 141942"))

#commandline_options = c("-b -g -p 1 110 136557 136557 -p 1 108 141942 141942 -p 1 108 149478 149478"))

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created
input_tec_data = IOin_tec_std(start = "2017 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")


```

RSS - run model in parallel 

```{r Run RHESSYS in Parallel using foreach RSS 2, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:validationruns, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = toprss[i,]$m,
                            k = toprss[i,]$k,
                            soil_dep= toprss[i,]$soil_dep,
                            m_v = toprss[i,]$m_v,
                            k_v = toprss[i,]$k_v,
                            gw1 = toprss[i,]$gw1,
                            gw2 = toprss[i,]$gw2,
                            pa = toprss[i,]$pa,
                            po = toprss[i,]$po,
                            vgseng1 = toprss[i,]$vgseng1,
                            vgseng2 = toprss[i,]$vgseng2,
                            vgseng3 = toprss[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

RSS - read n runs, create table and append to table

```{r}
# Read in RHESSys Validation runs
for(i in 1:validationruns) { assign(paste0("cwws32valrss2_run",i), readin_rhessys_output(paste0("out/cwws32valrss2_run",i)))}

##merge calibration runs with observed so dates match up, instead of subsetting 

for(i in 1:validationruns) { assign(paste0("valmergesm",i), merge(obsws32smvalclean,eval(parse(text = paste0("cwws32valrss2_run",i,"$pd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("valsubsetsm",i),eval(parse(text = paste0("valmergesm",i)))[eval(parse(text = paste0("valmergesm",i,"$date"))) >= Valdates[1] & eval(parse(text = paste0("valmergesm",i,"$date"))) <= Valdates[2], ])}


valmergesm1


validationsmNSElistsite2<- c()
validationsmlnNSElistsite2<- c()
validationsmKGElistsite2<- c()


#for(i in 1:n) {  assign(paste0("vsmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
#  valsmNSElist[[i]]<- eval(parse(text = paste0("vsmNSEobs",i))) }

#for(i in 1:n) {  assign(paste0("vsmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
#  valsmlnNSElist[[i]]<- eval(parse(text = paste0("vsmlnNSEobs",i))) }

for(i in 1:validationruns) {  assign(paste0("vsmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")))), obs = as.numeric(eval(parse(text = paste0("valmergesm",i,"$Site2"))))))
  validationsmKGElistsite2[[i]]<- eval(parse(text = paste0("vsmKGEobs",i))) }


validationsmKGElistsite2






```

RSS - Explore Site 2

```{r}

'Exploring Site 2 RSS'


cwws32valrss2_run1

{plot(cwws32valrss2_run1$bd$date, (cwws32valrss2_run1$bd$rz_storage/cwws32valrss2_run1$bd$rootdepth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm1$Date,valmergesm1$Site2, col = 'BLUE', lty = 3)}



{plot(cwws32valrss2_run3$bd$date, (cwws32valrss2_run3$bd$rz_storage/cwws32valrss2_run3$bd$rootdepth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm3$Date,valmergesm3$Site2, col = 'BLUE', lty = 3)}

paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")

plot((valmergesm3$root_zone.S*valmergesm3$potential_rz_store)/(valmergesm3$root.depth), type = "l")
plot(valmergesm3$Date, (valmergesm3$rz_storage/valmergesm3$root.depth), type = "l")
plot(valmergesm3$Date, valmergesm3$Site2, type = "l")


{plot(cwws32valrss2_run3$pd$date, (cwws32valrss2_run3$pd$rz_storage/cwws32valrss2_run3$pd$root.depth), type = 'l', ylim = c(0.0,0.26))
lines(valmergesm3$Date,valmergesm3$Site2, col = 'BLUE', lty = 3)}


{plot(cwws32valrss2_run3$pd$date, ((cwws32valrss2_run3$pd$root_zone.S*cwws32valrss2_run3$pd$potential_rz_store)/cwws32valrss2_run3$pd$root.depth), type = 'l', ylim = c(0.0,0.26))
lines(valmergesm3$Date,valmergesm3$Site2, col = 'BLUE', lty = 3)}

paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")


{plot(cwws32valrss2_run3$bd$date, (cwws32valrss2_run3$bd$rz_storage/cwws32valrss2_run3$bd$rootdepth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm3$Date,valmergesm3$Site2, col = 'BLUE', lty = 3)}

{plot(cwws32valrss2_run43$pd$date, (cwws32valrss2_run43$pd$rz_storage/cwws32valrss2_run43$pd$root.depth), type = 'l', ylim = c(0.0,0.26))
lines(valmergesm43$Date,valmergesm43$Site2, col = 'BLUE', lty = 3)}

{plot(cwws32valrss2_run43$bd$date, (cwws32valrss2_run43$bd$rz_storage/cwws32valrss2_run43$bd$rootdepth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm1$Date,valmergesm1$Site2, col = 'BLUE', lty = 3)}

```

prepare to run model 20 times for patch 3 - only for validation time series

```{r}

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32dsm.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32dsm",
  flowtable = "CWWS32dsm1.flow",
  start = "2015 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32valrss3",
 commandline_options = c("-b -p 1 108 149478 149478"))

#commandline_options = c("-b -g -p 1 110 136557 136557 -p 1 108 141942 141942 -p 1 108 149478 149478"))

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created
input_tec_data = IOin_tec_std(start = "2017 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")


```

RSS - run model in parallel

```{r Run RHESSYS in Parallel using foreach RSS 3, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:validationruns, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = toprss[i,]$m,
                            k = toprss[i,]$k,
                            soil_dep= toprss[i,]$soil_dep,
                            m_v = toprss[i,]$m_v,
                            k_v = toprss[i,]$k_v,
                            gw1 = toprss[i,]$gw1,
                            gw2 = toprss[i,]$gw2,
                            pa = toprss[i,]$pa,
                            po = toprss[i,]$po,
                            vgseng1 = toprss[i,]$vgseng1,
                            vgseng2 = toprss[i,]$vgseng2,
                            vgseng3 = toprss[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

RSS - read n runs, create table and append to table

```{r}
# Read in RHESSys Validation runs
for(i in 1:validationruns) { assign(paste0("cwws32valrss3_run",i), readin_rhessys_output(paste0("out/cwws32valrss3_run",i)))}

##merge calibration runs with observed so dates match up, instead of subsetting 

for(i in 1:validationruns) { assign(paste0("valmergesm",i), merge(obsws32smvalclean,eval(parse(text = paste0("cwws32valrss3_run",i,"$pd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("valsubsetsm",i),eval(parse(text = paste0("valmergesm",i)))[eval(parse(text = paste0("valmergesm",i,"$date"))) >= Valdates[1] & eval(parse(text = paste0("valmergesm",i,"$date"))) <= Valdates[2], ])}


validationsmNSElistsite3<- c()
validationsmlnNSElistsite3<- c()
validationsmKGElistsite3<- c()

#for(i in 1:n) {  assign(paste0("vsmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
#  valsmNSElist[[i]]<- eval(parse(text = paste0("vsmNSEobs",i))) }

#for(i in 1:n) {  assign(paste0("vsmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
#  valsmlnNSElist[[i]]<- eval(parse(text = paste0("vsmlnNSEobs",i))) }

for(i in 1:validationruns) {  assign(paste0("vsmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")))), obs = as.numeric(eval(parse(text = paste0("valmergesm",i,"$Site3"))))))
  validationsmKGElistsite3[[i]]<- eval(parse(text = paste0("vsmKGEobs",i))) }


validationsmKGElistsite3

valmergesm2

 
```

RSS - Explore Site 3

```{r}

'Exploring Site 3 RSS'


cwws32valrss3_run1

{plot(cwws32valrss3_run1$bd$date, (cwws32valrss3_run1$bd$rz_storage/cwws32valrss3_run1$bd$rootdepth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm1$Date,valmergesm1$Site3, col = 'BLUE', lty = 3)}



{plot(cwws32valrss3_run3$bd$date, (cwws32valrss3_run3$bd$rz_storage/cwws32valrss3_run3$bd$rootdepth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm3$Date,valmergesm3$Site3, col = 'BLUE', lty = 3)}

paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")

plot((valmergesm3$root_zone.S*valmergesm3$potential_rz_store)/(valmergesm3$root.depth), type = "l")
plot(valmergesm3$Date, (valmergesm3$rz_storage/valmergesm3$root.depth), type = "l")
plot(valmergesm3$Date, valmergesm3$Site3, type = "l")


{plot(cwws32valrss3_run3$pd$date, (cwws32valrss3_run3$pd$rz_storage/cwws32valrss3_run3$pd$root.depth), type = 'l', ylim = c(0.0,0.45))
lines(valmergesm3$Date,valmergesm3$Site3, col = 'BLUE', lty = 3)}


{plot(cwws32valrss3_run3$pd$date, ((cwws32valrss3_run3$pd$root_zone.S*cwws32valrss3_run3$pd$potential_rz_store)/cwws32valrss3_run3$pd$root.depth), type = 'l', ylim = c(0.0,0.45))
lines(valmergesm3$Date,valmergesm3$Site3, col = 'BLUE', lty = 3)}

## based on landscape position the previous two figures differ, the second figure does not count inundation as "0" VWC

#paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")


{plot(cwws32valrss3_run3$bd$date, (cwws32valrss3_run3$bd$rz_storage/cwws32valrss3_run3$bd$rootdepth), type = 'l', ylim = c(0.0,0.45))
lines(valmergesm3$Date,valmergesm3$Site3, col = 'BLUE', lty = 3)}

{plot(cwws32valrss3_run43$pd$date, (cwws32valrss3_run43$pd$rz_storage/cwws32valrss3_run43$pd$root.depth), type = 'l', ylim = c(0.0,0.35))
lines(valmergesm43$Date,valmergesm43$Site3, col = 'BLUE', lty = 3)}

{plot(cwws32valrss3_run43$bd$date, (cwws32valrss3_run43$bd$rz_storage/cwws32valrss3_run43$bd$rootdepth), type = 'l', ylim = c(0.12,0.26))
lines(valmergesm1$Date,valmergesm1$Site3, col = 'BLUE', lty = 3)}

```


RSS - merge all 3 sites

```{r}

threesitevalidation1<- data.frame(cbind(site1=as.numeric(validationsmKGElistsite1),site2=as.numeric(validationsmKGElistsite2),site3=as.numeric(validationsmKGElistsite3)))


threesitevalidation<-threesitevalidation1

threesitevalidation$allsites<- rowMeans(threesitevalidation1,na.rm=FALSE)

threesitevalidation


boxplot(threesitevalidation1, main = "Boxplot of Patch Specific Soil Moisture KGE - RSS")
boxplot(threesitevalidation, main = "Boxplot of Patch Specific Soil Moisture KGE - RSS")



plot(validationsmKGElistsite1,validationsmKGElistsite3)

write.csv(threesitevalidation,'threesitevalidationrss.csv')


```

STATIC

run model n times for patch 1 - only for validation time series

```{r}

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32static.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32static",
  flowtable = "CWWS32static1.flow",
  start = "2015 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32valstatic1",
commandline_options = c("-b -p 1 110 136557 136557"))

#commandline_options = c("-b -g -p 1 110 136557 136557 -p 1 108 141942 141942 -p 1 108 149478 149478"))

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created
input_tec_data = IOin_tec_std(start = "2017 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")


```

run static

```{r Run RHESSYS in Parallel using foreach STATIC 1, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:validationruns, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = topstatic[i,]$m,
                            k = topstatic[i,]$k,
                            soil_dep= topstatic[i,]$soil_dep,
                            m_v = topstatic[i,]$m_v,
                            k_v = topstatic[i,]$k_v,
                            gw1 = topstatic[i,]$gw1,
                            gw2 = topstatic[i,]$gw2,
                            pa = topstatic[i,]$pa,
                            po = topstatic[i,]$po,
                            vgseng1 = topstatic[i,]$vgseng1,
                            vgseng2 = topstatic[i,]$vgseng2,
                            vgseng3 = topstatic[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

read 20 runs, create table and append to table for patch 1

```{r}
# Read in RHESSys Validation runs
for(i in 1:validationruns) { assign(paste0("cwws32valstatic1_run",i), readin_rhessys_output(paste0("out/cwws32valstatic1_run",i)))}


plot(cwws32valstatic1_run1$pd$date,cwws32valstatic1_run1$pd$rz_storage/cwws32valstatic1_run1$pd$root.depth)



##merge calibration runs with observed so dates match up, instead of subsetting 

for(i in 1:validationruns) { assign(paste0("valmergesm",i), merge(obsws32smvalclean,eval(parse(text = paste0("cwws32valstatic1_run",i,"$pd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("valsubsetsm",i),eval(parse(text = paste0("valmergesm",i)))[eval(parse(text = paste0("valmergesm",i,"$date"))) >= Valdates[1] & eval(parse(text = paste0("valmergesm",i,"$date"))) <= Valdates[2], ])}


valmergesm1


validationsmNSElistsite1<- c()
validationsmlnNSElistsite1<- c()
validationsmKGElistsite1<- c()


#for(i in 1:n) {  assign(paste0("vsmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
#  valsmNSElist[[i]]<- eval(parse(text = paste0("vsmNSEobs",i))) }

#for(i in 1:n) {  assign(paste0("vsmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
#  valsmlnNSElist[[i]]<- eval(parse(text = paste0("vsmlnNSEobs",i))) }

for(i in 1:validationruns) {  assign(paste0("vsmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")))), obs = as.numeric(eval(parse(text = paste0("valmergesm",i,"$Site1"))))))
  validationsmKGElistsite1[[i]]<- eval(parse(text = paste0("vsmKGEobs",i))) }


validationsmKGElistsite1



```

prepare to run model 20 times for patch 2 - only for validation time series

```{r}

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32static.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32static",
  flowtable = "CWWS32static1.flow",
  start = "2015 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32valstatic2",
 commandline_options = c("-b -p 1 108 141942 141942"))

#commandline_options = c("-b -g -p 1 110 136557 136557 -p 1 108 141942 141942 -p 1 108 149478 149478"))

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created
input_tec_data = IOin_tec_std(start = "2017 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")


```

run model in parallel 

```{r Run RHESSYS in Parallel using foreach STATIC 2, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:validationruns, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = topstatic[i,]$m,
                            k = topstatic[i,]$k,
                            soil_dep= topstatic[i,]$soil_dep,
                            m_v = topstatic[i,]$m_v,
                            k_v = topstatic[i,]$k_v,
                            gw1 = topstatic[i,]$gw1,
                            gw2 = topstatic[i,]$gw2,
                            pa = topstatic[i,]$pa,
                            po = topstatic[i,]$po,
                            vgseng1 = topstatic[i,]$vgseng1,
                            vgseng2 = topstatic[i,]$vgseng2,
                            vgseng3 = topstatic[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

read 20 runs, create table and append to table

```{r}
# Read in RHESSys Validation runs
for(i in 1:validationruns) { assign(paste0("cwws32valstatic2_run",i), readin_rhessys_output(paste0("out/cwws32valstatic2_run",i)))}

##merge calibration runs with observed so dates match up, instead of subsetting 

for(i in 1:validationruns) { assign(paste0("valmergesm",i), merge(obsws32smvalclean,eval(parse(text = paste0("cwws32valstatic2_run",i,"$pd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("valsubsetsm",i),eval(parse(text = paste0("valmergesm",i)))[eval(parse(text = paste0("valmergesm",i,"$date"))) >= Valdates[1] & eval(parse(text = paste0("valmergesm",i,"$date"))) <= Valdates[2], ])}


valmergesm1


validationsmNSElistsite2<- c()
validationsmlnNSElistsite2<- c()
validationsmKGElistsite2<- c()


#for(i in 1:n) {  assign(paste0("vsmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
#  valsmNSElist[[i]]<- eval(parse(text = paste0("vsmNSEobs",i))) }

#for(i in 1:n) {  assign(paste0("vsmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
#  valsmlnNSElist[[i]]<- eval(parse(text = paste0("vsmlnNSEobs",i))) }

for(i in 1:validationruns) {  assign(paste0("vsmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")))), obs = as.numeric(eval(parse(text = paste0("valmergesm",i,"$Site2"))))))
  validationsmKGElistsite2[[i]]<- eval(parse(text = paste0("vsmKGEobs",i))) }


validationsmKGElistsite2



```

run model 20 times for patch 3 - only for validation time series

```{r}

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32static.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32static",
  flowtable = "CWWS32static1.flow",
  start = "2015 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32valstatic3",
 commandline_options = c("-b -p 1 108 149478 149478"))

#commandline_options = c("-b -g -p 1 110 136557 136557 -p 1 108 141942 141942 -p 1 108 149478 149478"))

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created
input_tec_data = IOin_tec_std(start = "2017 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")


```

run model in parallel

```{r Run RHESSYS in Parallel using foreach STATIC 3, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:validationruns, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = topstatic[i,]$m,
                            k = topstatic[i,]$k,
                            soil_dep= topstatic[i,]$soil_dep,
                            m_v = topstatic[i,]$m_v,
                            k_v = topstatic[i,]$k_v,
                            gw1 = topstatic[i,]$gw1,
                            gw2 = topstatic[i,]$gw2,
                            pa = topstatic[i,]$pa,
                            po = topstatic[i,]$po,
                            vgseng1 = topstatic[i,]$vgseng1,
                            vgseng2 = topstatic[i,]$vgseng2,
                            vgseng3 = topstatic[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

read 20 runs, create table and append to table

```{r}
# Read in RHESSys Validation runs
for(i in 1:validationruns) { assign(paste0("cwws32valstatic3_run",i), readin_rhessys_output(paste0("out/cwws32valstatic3_run",i)))}

##merge calibration runs with observed so dates match up, instead of subsetting 

for(i in 1:validationruns) { assign(paste0("valmergesm",i), merge(obsws32smvalclean,eval(parse(text = paste0("cwws32valstatic3_run",i,"$pd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("valsubsetsm",i),eval(parse(text = paste0("valmergesm",i)))[eval(parse(text = paste0("valmergesm",i,"$date"))) >= Valdates[1] & eval(parse(text = paste0("valmergesm",i,"$date"))) <= Valdates[2], ])}


validationsmNSElistsite3<- c()
validationsmlnNSElistsite3<- c()
validationsmKGElistsite3<- c()

#for(i in 1:n) {  assign(paste0("vsmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
#  valsmNSElist[[i]]<- eval(parse(text = paste0("vsmNSEobs",i))) }

#for(i in 1:n) {  assign(paste0("vsmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
#  valsmlnNSElist[[i]]<- eval(parse(text = paste0("vsmlnNSEobs",i))) }

for(i in 1:validationruns) {  assign(paste0("vsmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")))), obs = as.numeric(eval(parse(text = paste0("valmergesm",i,"$Site3"))))))
  validationsmKGElistsite3[[i]]<- eval(parse(text = paste0("vsmKGEobs",i))) }


validationsmKGElistsite3

valmergesm2
 
```

merge all 3 sites 

```{r}

threesitevalidation1<- data.frame(cbind(site1=as.numeric(validationsmKGElistsite1),site2=as.numeric(validationsmKGElistsite2),site3=as.numeric(validationsmKGElistsite3)))


threesitevalidation<-threesitevalidation1

threesitevalidation$allsites<- rowMeans(threesitevalidation1,na.rm=FALSE)

threesitevalidation


boxplot(threesitevalidation1, main = "Boxplot of Patch Specific Soil Moisture KGE - Static")
boxplot(threesitevalidation, main = "Boxplot of Patch Specific Soil Moisture KGE - Static")



plot(validationsmKGElistsite1,validationsmKGElistsite3)

write.csv(threesitevalidation,'threesitevalidationstatic.csv')


```

SSURGO

run model 20 times for patch 1 - only for validation time series

```{r}

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32ssurgo.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32ssurgo",
  flowtable = "CWWS32ssurgo1.flow",
  start = "2015 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32valssurgo",
commandline_options = c("-b -p 1 110 136557 136557"))

#commandline_options = c("-b -g -p 1 110 136557 136557 -p 1 108 141942 141942 -p 1 108 149478 149478"))

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created
input_tec_data = IOin_tec_std(start = "2017 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")


```

run SSURGO

```{r Run RHESSYS in Parallel using foreach SSURGO 1, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:validationruns, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = topssurgo[i,]$m,
                            k = topssurgo[i,]$k,
                            soil_dep= topssurgo[i,]$soil_dep,
                            m_v = topssurgo[i,]$m_v,
                            k_v = topssurgo[i,]$k_v,
                            gw1 = topssurgo[i,]$gw1,
                            gw2 = topssurgo[i,]$gw2,
                            pa = topssurgo[i,]$pa,
                            po = topssurgo[i,]$po,
                            vgseng1 = topssurgo[i,]$vgseng1,
                            vgseng2 = topssurgo[i,]$vgseng2,
                            vgseng3 = topssurgo[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

read 20 runs, create table and append to table for site 1

```{r}

setwd(system.file("extdata/", package = "RHESSysIOinR"))



getwd()

validationruns <- 200

# Read in RHESSys Validation runs
for(i in 1:validationruns) {assign(paste0("cwws32valssurgo_run",i), readin_rhessys_output(paste0("out/cwws32valssurgo_run",i)))}

plot(cwws32valssurgo_run1$pd$date,cwws32valssurgo_run1$pd$rz_storage/cwws32valssurgo_run1$pd$root.depth)





##merge calibration runs with observed so dates match up, instead of subsetting 

for(i in 1:validationruns) { assign(paste0("valmergesm",i), merge(obsws32smvalclean,eval(parse(text = paste0("cwws32valssurgo_run",i,"$pd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("valsubsetsm",i),eval(parse(text = paste0("valmergesm",i)))[eval(parse(text = paste0("valmergesm",i,"$date"))) >= Valdates[1] & eval(parse(text = paste0("valmergesm",i,"$date"))) <= Valdates[2], ])}


valmergesm1


validationsmNSElistsite1<- c()
validationsmlnNSElistsite1<- c()
validationsmKGElistsite1<- c()


#for(i in 1:n) {  assign(paste0("vsmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
#  valsmNSElist[[i]]<- eval(parse(text = paste0("vsmNSEobs",i))) }

#for(i in 1:n) {  assign(paste0("vsmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
#  valsmlnNSElist[[i]]<- eval(parse(text = paste0("vsmlnNSEobs",i))) }

for(i in 1:validationruns) {  assign(paste0("vsmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")))), obs = as.numeric(eval(parse(text = paste0("valmergesm",i,"$Site1"))))))
  validationsmKGElistsite1[[i]]<- eval(parse(text = paste0("vsmKGEobs",i))) }


validationsmKGElistsite1



```

prepare to run model n times for patch 2 - only for validation time series

```{r}

validationruns <- 200

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32ssurgo.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32ssurgo",
  flowtable = "CWWS32ssurgo1.flow",
  start = "2015 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32valssurgo2",
 commandline_options = c("-b -p 1 108 141942 141942"))

#commandline_options = c("-b -g -p 1 110 136557 136557 -p 1 108 141942 141942 -p 1 108 149478 149478"))

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created
input_tec_data = IOin_tec_std(start = "2017 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")


```

run model in parallel 

```{r Run RHESSYS in Parallel using foreach SSURGO 2, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:validationruns, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = topssurgo[i,]$m,
                            k = topssurgo[i,]$k,
                            soil_dep= topssurgo[i,]$soil_dep,
                            m_v = topssurgo[i,]$m_v,
                            k_v = topssurgo[i,]$k_v,
                            gw1 = topssurgo[i,]$gw1,
                            gw2 = topssurgo[i,]$gw2,
                            pa = topssurgo[i,]$pa,
                            po = topssurgo[i,]$po,
                            vgseng1 = topssurgo[i,]$vgseng1,
                            vgseng2 = topssurgo[i,]$vgseng2,
                            vgseng3 = topssurgo[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

read 20 runs, create table and append to table for site 2

```{r}
# Read in RHESSys Validation runs
for(i in 1:validationruns) { assign(paste0("cwws32valssurgo2_run",i), readin_rhessys_output(paste0("out/cwws32valssurgo2_run",i)))}

##merge calibration runs with observed so dates match up, instead of subsetting 

for(i in 1:validationruns) { assign(paste0("valmergesm",i), merge(obsws32smvalclean,eval(parse(text = paste0("cwws32valssurgo2_run",i,"$pd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("valsubsetsm",i),eval(parse(text = paste0("valmergesm",i)))[eval(parse(text = paste0("valmergesm",i,"$date"))) >= Valdates[1] & eval(parse(text = paste0("valmergesm",i,"$date"))) <= Valdates[2], ])}


valmergesm1


validationsmNSElistsite2<- c()
validationsmlnNSElistsite2<- c()
validationsmKGElistsite2<- c()


#for(i in 1:n) {  assign(paste0("vsmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
#  valsmNSElist[[i]]<- eval(parse(text = paste0("vsmNSEobs",i))) }

#for(i in 1:n) {  assign(paste0("vsmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
#  valsmlnNSElist[[i]]<- eval(parse(text = paste0("vsmlnNSEobs",i))) }

for(i in 1:validationruns) {  assign(paste0("vsmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")))), obs = as.numeric(eval(parse(text = paste0("valmergesm",i,"$Site2"))))))
  validationsmKGElistsite2[[i]]<- eval(parse(text = paste0("vsmKGEobs",i))) }


 validationsmKGElistsite2



```

run model 20 times for patch 3 - only for validation time series

```{r}

input_rhessys = IOin_rhessys_input(
  version = rh_path,
  tec_file = "tecfiles/tec_daily",
  world_file = "CWWS32ssurgo.world.Y2018M10D31H1.state.Y2018M10D31H1.state",
  world_hdr_prefix = "CWWS32ssurgo",
  flowtable = "CWWS32ssurgo1.flow",
  start = "2015 11 1 1",
  end = "2018 11 1 1",
  output_folder = "out",
  output_prefix = "cwws32valssurgo3",
 commandline_options = c("-b -p 1 108 149478 149478"))

#commandline_options = c("-b -g -p 1 110 136557 136557 -p 1 108 141942 141942 -p 1 108 149478 149478"))

## TEC file dictates model output, begin output a year in to allow model SM to stabilize
# do not output_state or worldfile may be overwritten as output is created
input_tec_data = IOin_tec_std(start = "2017 11 1 1",
                              end = "2018 11 1 1",
                              output_state = FALSE)

input_hdr = IOin_hdr(
  basin = "defs/basin.def",
  hillslope = "defs/hillslope.def",
  zone = "defs/zone.def",
  soil = c("defs/soil_clay.def","defs/soil_clayloam.def","defs/soil_loam.def","defs/soil_loamysand.def","defs/soil_rock.def","defs/soil_sand.def","defs/soil_sandyclay.def","defs/soil_sandyclayloam.def","defs/soil_sandyloam.def","defs/soil_silt.def","defs/soil_siltyclay.def","defs/soil_siltyclayloam.def","defs/soil_siltyloam.def","defs/soil_water.def", "defs/soil_shallowloam.def", "defs/soil_shallowsandyclayloam.def", "defs/soil_shallowsandyloam.def"),
  landuse = "defs/lu_undev.def",
  stratum = c("defs/veg_deciduous/veg_deciduous.def","defs/veg_evergreen/veg_evergreen.def","defs/veg_deciduous_BES.def","defs/veg_eucalypt.def","defs/veg_grass.def","defs/veg_lawn_2cm.def","defs/veg_lawn_5cm.def","defs/veg_lawn_10cm.def","defs/veg_nonveg.def"),
  basestations = "clim/cwtws32local.base")


```

run model in parallel

```{r Run RHESSYS in Parallel using foreach SSURGO 3, eval=FALSE, include=FALSE}
n.cores <- parallel::detectCores() - 4  
  
my.cluster <- parallel::makeCluster(
    n.cores, 
    type = "PSOCK"
  )
doParallel::registerDoParallel(cl = my.cluster)

start_time = Sys.time()
  
  foreach(i = 1:validationruns, .packages = 'RHESSysIOinR') %dopar% {
    
    stdpars<- IOin_std_pars(m = topssurgo[i,]$m,
                            k = topssurgo[i,]$k,
                            soil_dep= topssurgo[i,]$soil_dep,
                            m_v = topssurgo[i,]$m_v,
                            k_v = topssurgo[i,]$k_v,
                            gw1 = topssurgo[i,]$gw1,
                            gw2 = topssurgo[i,]$gw2,
                            pa = topssurgo[i,]$pa,
                            po = topssurgo[i,]$po,
                            vgseng1 = topssurgo[i,]$vgseng1,
                            vgseng2 = topssurgo[i,]$vgseng2,
                            vgseng3 = topssurgo[i,]$vgseng3)
    
    run_rhessys_single(input_rhessys = input_rhessys,
                       hdr_files = input_hdr,
                       tec_data = input_tec_data,
                       std_pars = stdpars,
                       runID = i)
  } 
  
  end_time = Sys.time()
  end_time - start_time
```

read 20 runs, create table and append to table for site 3

```{r}
# Read in RHESSys Validation runs
for(i in 1:validationruns) { assign(paste0("cwws32valssurgo3_run",i), readin_rhessys_output(paste0("out/cwws32valssurgo3_run",i)))}

##merge calibration runs with observed so dates match up, instead of subsetting 

for(i in 1:validationruns) { assign(paste0("valmergesm",i), merge(obsws32smvalclean,eval(parse(text = paste0("cwws32valssurgo3_run",i,"$pd"))), by.x = "Date", by.y="date", all = FALSE))
  assign(paste0("valsubsetsm",i),eval(parse(text = paste0("valmergesm",i)))[eval(parse(text = paste0("valmergesm",i,"$date"))) >= Valdates[1] & eval(parse(text = paste0("valmergesm",i,"$date"))) <= Valdates[2], ])}


validationsmNSElistsite3<- c()
validationsmlnNSElistsite3<- c()
validationsmKGElistsite3<- c()

#for(i in 1:n) {  assign(paste0("vsmNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture"))))))
#  valsmNSElist[[i]]<- eval(parse(text = paste0("vsmNSEobs",i))) }

#for(i in 1:n) {  assign(paste0("vsmlnNSEobs",i), NSE(sim = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$rz_storage","/valsubsetsm",i,"$rootdepth")))), obs = as.numeric(eval(parse(text = paste0("valsubsetsm",i,"$mergedsoilmoisture")))), FUN = log, epsilon = "Pushpalatha2012", na.rm=TRUE))
#  valsmlnNSElist[[i]]<- eval(parse(text = paste0("vsmlnNSEobs",i))) }

for(i in 1:validationruns) {  assign(paste0("vsmKGEobs",i), KGE(sim = as.numeric(eval(parse(text = paste0("((valmergesm",i,"$root_zone.S","*valmergesm",i,"$potential_rz_store)","/valmergesm",i,"$root.depth)")))), obs = as.numeric(eval(parse(text = paste0("valmergesm",i,"$Site3"))))))
  validationsmKGElistsite3[[i]]<- eval(parse(text = paste0("vsmKGEobs",i))) }


validationsmKGElistsite3

valmergesm2
 
```

merge all 3 sites

```{r}

threesitevalidation1<- data.frame(cbind(site1=as.numeric(validationsmKGElistsite1),site2=as.numeric(validationsmKGElistsite2),site3=as.numeric(validationsmKGElistsite3)))


threesitevalidation<-threesitevalidation1

threesitevalidation$allsites<- rowMeans(threesitevalidation1,na.rm=FALSE)

threesitevalidation


boxplot(threesitevalidation1, main = "Boxplot of Patch Specific Root Zone Soil Moisture KGE - SSURGO")
boxplot(threesitevalidation, main = "Boxplot of Patch Specific Root Zone Soil Moisture KGE - SSURGO")



plot(validationsmKGElistsite1,validationsmKGElistsite3)

write.csv(threesitevalidation,'threesitevalidationssurgo.csv')


```

Group by group
color by site
plot kge on y axis
plot group on x axis

```{r}

ssurgovalidation<- read.csv("threesitevalidationssurgo.csv")
rssvalidation<- read.csv("threesitevalidationrss.csv")
staticvalidation<- read.csv("threesitevalidationstatic.csv")

staticvalidation$group <- 'Static'
rssvalidation$group <- 'RSS'
ssurgovalidation$group<- 'SSURGO'

combinedvalidation <- rbind(staticvalidation, rssvalidation, ssurgovalidation)


combinedvalidationlong1<- data.frame("KGE" = combinedvalidation$site1, "group" = combinedvalidation$group)
combinedvalidationlong2<- data.frame("KGE" = combinedvalidation$site2, "group" = combinedvalidation$group)
combinedvalidationlong3<- data.frame("KGE" = combinedvalidation$site3, "group" = combinedvalidation$group)
combinedvalidationlong4<- data.frame("KGE" = combinedvalidation$allsites, "group" = combinedvalidation$group)


combinedvalidationlong1$site = '1'
combinedvalidationlong2$site = '2'
combinedvalidationlong3$site = '3'
combinedvalidationlong4$site = 'All Sites'




combinedvalidationlong<- rbind(combinedvalidationlong1,combinedvalidationlong2, combinedvalidationlong3, combinedvalidationlong4)

combinedvalidationlong


#Remove NA values so that boxplot will work

validationnona<- subset(combinedvalidationlong,!is.na(combinedvalidationlong$KGE))


threesitevalidationplot <- ggplot(validationnona, aes(group, y = KGE, fill = site))+ geom_boxplot()+ ylab("Soil Moisture KGE - Validation") +xlab("Soil Map Input")+ ggtitle("Patch Specific Soil Moisture KGE For ALL Calibration Runs, NA Excluded")+geom_hline(yintercept=-0.41,linetype=2, col = 'RED')+ scale_y_continuous(breaks=seq(-6,1,1))+ theme_minimal()

threesitevalidationplot


validationnona




```

